### 2019-03-15 paper.tex
public branch made

\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{caption}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\newlist{inlinelist}{enumerate*}{1}
\setlist*[inlinelist]{label=(\arabic*)}
\usepackage[totalwidth=450pt, totalheight=630pt]{geometry}
\usepackage{graphicx}
\PassOptionsToPackage{hyphens}{url} % pass options to url autoloaded by hyperref
\usepackage[pdfencoding=auto, psdextra]{hyperref} % hyperref must be loaded before cleveref
\usepackage{mathrsfs}
\usepackage{multirow}
\usepackage[round]{natbib} % natbib must be loaded before algorithm2e
\usepackage[linesnumbered, ruled]{algorithm2e} % algorithm2e must be loaded before cleveref
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{verbatim}
\usepackage{xcolor}

\interfootnotelinepenalty=10000

\definecolor{deep-blue}{HTML}{2c7bb6}
\colorlet{mid-blue}{deep-blue!25}

\captionsetup{width=0.8\textwidth}

\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{lemma}[corollary]{Lemma}
\newtheorem{proposition}[corollary]{Proposition}
\newtheorem{theorem}[corollary]{Theorem}

\theoremstyle{definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}
\newtheorem*{remark}{Remark}

\newtheoremstyle{custom}{}{}{\itshape}{}{\bfseries}{.}{.5em}{\thmnote{#3}}
\theoremstyle{custom}
\newtheorem*{customthm}{Theorem}

\setlength{\tabcolsep}{1em}
\setlist{listparindent=\parindent, parsep=0pt}

\newcommand{\EE}{\mathbb{E}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\cH}{\mathcal{H}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\se}{se}
\DeclareMathOperator{\sgn}{sign}
\DeclareMathOperator{\Binomial}{Binomial}
\DeclareMathOperator{\Uniform}{Uniform}

\newcommand{\hdelta}{\hat{\delta}}
\newcommand{\hmu}{\hat{\mu}}
\newcommand{\hsigma}{\hat{\sigma}}
\newcommand{\htheta}{\hat{\theta}}
\newcommand{\FDPd}{\text{FDP}_\text{dir}}
\newcommand{\hFDPd}{\widehat{\text{FDP}}_\text{dir}}
\newcommand{\ao}{\alpha_0}
\newcommand{\lest}{\le_\text{st}}
\newcommand{\gest}{\ge_\text{st}}

\newcommand{\WFcomment}[1]{{\color{red!40!gray} (WF: #1)}}
\newcommand{\KHcomment}[1]{{\color{green!40!gray} (KH: #1)}}

% Uncomment this line to get rid of my comments
% \renewcommand{\WFcomment}[1]{}
% \renewcommand{\KHcomment}[1]{}

\graphicspath{{./fig/}}

\begin{document}

\title{Statistical Methods for Replicability Assessment}
\date{\today}
\author{
  Kenneth Hung\thanks{Department of Mathematics, University of California, Berkeley} \and
  William Fithian\thanks{Department of Statistics, University of California, Berkeley}
}
\maketitle

\begin{abstract}
  Large-scale replication studies like the Reproducibility Project: Psychology (RP:P) provide invaluable systematic data on scientific replicability, but most analyses and interpretations of the data fail to agree on the definition of ``replicability'' and disentangle the inexorable consequences of known selection bias from competing explanations. We discuss three concrete definitions of replicability based on
  \begin{inlinelist}
    \item whether published findings about the signs of effects are mostly correct,
    \item how effective replication studies are in reproducing whatever true effect size was present in the original experiment, and
    \item whether true effect sizes tend to diminish in replication.
  \end{inlinelist}
  We apply techniques from multiple testing and post-selection inference to develop new methods that answer these questions while explicitly accounting for selection bias. Re-analyzing the RP:P data, we estimate that $22$ out of $68$ ($32\%$) original directional claims were false (upper confidence bound $47\%$); by comparison, we estimate that among claims significant at the stricter significance threshold $0.005$, only $2.2$ out of $33$ ($7\%$) were directionally false (upper confidence bound $18\%$). In addition, we compute selection-adjusted confidence intervals for the difference in effect size between original and replication studies and, after adjusting for multiplicity, identify five ($11\%$) which exclude zero (exact replication). We estimate that the effect size declined by at least $20\%$ in the replication study relative to the original study in $16$ of the $46$ ($35\%$) study pairs (lower confidence bound $11\%$). Our methods make no distributional assumptions about the true effect sizes.
\end{abstract}

\section{Introduction}
\label{sec:intro}

  Growing concerns about selection bias, $p$-hacking, and other questionable research practices (QRPs) have raised urgent questions about the reliability of scientific findings. While concerns about replicability cut across scientific disciplines, psychologists have led large-scale efforts to assess the replicability of their own field. The largest and most systematic of these efforts has been the Reproducibility Project:\ Psychology (RP:P),\footnote{In some parts of the literature, ``reproducibility'' has taken on a computational connotation, meaning only that other scientists can repeat the analysis using the original study's data; we will lean toward the more unambiguous term ``replicability.''} a major collaboration by several hundred psychologists to replicate a representative sample of 100 studies published in 2008 in three top psychology journals, {\em Psychological Science}, {\em Journal of Personality and Social Psychology}, and {\em Journal of Experimental Psychology: Learning, Memory, and Cognition}.\footnote{The test statistics, effect sizes and most pertinent information are all publicly available on at the Open Science Foundation website at \url{https://osf.io/ezcuj/}.}

  While the RP:P dataset is an invaluable resource, scientists disagree on how to quantify or measure replicability \citep{Goodman:2016bo,Amrhein:2017en}. \citet[OSC;][]{OpenScienceCollaboration:2015cn} reported three main metrics: it found that $64\%$ ($= 1 - 36\%$) of the replication studies did not find statistically significant results in the same direction as the original studies, that $53\%$ ($= 1 - 47\%$) of $95\%$ confidence intervals for the replication studies do not contain the point estimates for their corresponding original studies, and that $83\%$ of the effect size estimates declined from original studies to replications. All three summary statistics were widely reported as indicating a dire crisis for the credibility of experimental psychology research. For example, the {\em Washington Post} reported that RP:P ``affirms that the skepticism [of published results] was warranted'' \citep{Achenbach:2015vi}; the {\em Economist} noted that OSC ``managed to replicate satisfactorily the results of only $39\%$ of the studies investigated'' \citep{Anonymous:uoQKTVTm}; and the {\em New York Times} reported that ``more than half of the findings did not hold up when retested'' \citep{Carey:2015wp}.

  This negative gloss was challenged in a comment by \citet{Gilbert:2016he}, who criticized both the fidelity of some of the replications' experimental designs and the aptness of the metrics reported by \citet{OpenScienceCollaboration:2015cn}. In particular, \citeauthor{Gilbert:2016he}\ pointed out that, because there is sampling error in the replication point estimates, we should not expect $95\%$ of the estimates to fall into the replication confidence intervals even under ideal conditions. Moreover, any small or large variations in the true effect sizes between the original and replication studies could further deflate the expected fraction of ``successful replications,'' as measured in this way. \citeauthor{Gilbert:2016he}\ concluded that ``OSC seriously underestimated the reproducibility of psychological science,'' sparking further debate between defenders of OSC's conclusions \citep{Anderson:2016gs,Srivastava:2016,Nosek:2016} and the critics \citep{Gilbert:2016uv,Gilbert:2016th}.\footnote{While much of the ensuing discussion focused on the question of whether the confidence interval metric $53\%$ is too pessimistic, analogous criticisms apply to the ``significant replications'' metric of $64\%$ as well: the replication studies could be underpowered even when a true effect is present.}

  To determine whether OSC truly underestimated replicability, we must first pin down the rather slippery question of what ``replicability'' actually is. Although the three metrics used by OSC are simply descriptive statistics that do not purport to estimate any explicitly defined underlying quantity, we can loosely characterize the $64\%$, $53\%$ and $83\%$ numbers respectively as qualitative answers to three questions:
  \begin{description}
    \item[False directional claims.] {\em What fraction of the original studies were erroneous} in claiming that the true effect was nonzero, in the claimed direction (positive or negative)? \citet{Gelman:2000tg} called such mistakes {\em type S} errors.
    \item[Effect shift.] {\em How much do the effect sizes shift} from the original study to the replication study? We call the discrepancy between the original and replication effect {\em effect shift}.
    \item[Effect decline.] {\em What fraction of the effect sizes decline?} More precisely, what fraction of the true effect sizes shift in a direction opposite to the original claims when the studies were replicated, and by how much?
  \end{description}
  The first question concerns a type of {\em false discovery rate} (FDR) of the statistical hypotheses, viewing the field of social psychology as a collective enterprise in large-scale multiple testing: it quantifies the fraction of findings that would be confirmed if the exact same studies could be carried out again with much larger samples from the same populations. The second question concerns a basic form of repeatability: whether scientists are typically successful in closely replicating each others' experimental conditions, so that the true effect being measured is stable across different experiments. The third question builds upon the second question: whether true effect sizes tend systematically to attenuate in replications. An overall trend of declining true effects could suggest various interpretations, including systematic biases in the original experiments or failures by the replication teams to reproduce key experimental conditions that produced the original effects.

  As we will see, however, none of the three reported metrics can be taken at face value as {\em estimates} of the answers to the corresponding questions, due to the confounding factor of pervasive selection bias. By using techniques from multiple testing and post-selection inference, we will develop methods to rigorously address these questions without assuming a model for the prior distribution of effect sizes. For the RP:P data we estimate the rate of false directional claims at roughly $32\%$ among studies with $p < 0.05$, which would be considered unacceptably high in most multiple testing applications. By contrast, among studies with $p < 0.005$, a lower threshold proposed by \citet{Benjamin:2018gh}, our estimate drops to $7\%$, with an upper confidence bound of $18\%$. We also compute confidence intervals for the effect shift in each individual study pair and find that, after adjusting for multiplicity, about $11\%$ of the intervals exclude zero, an idealized null hypothesis of perfect replication. For effect decline, we find in aggregate that $35\%$ of the true effects declined, and $35\%$ declined by at least $20\%$.

  In addressing each question, we define our estimands in terms of the true effects present in the statistical populations actually sampled in each study. Because some studies may be biased or lack external validity --- for example, because of flaws in the study design, or because survey participants are unrepresentative of the broader population of scientific interest --- these effect sizes may not reflect the latent scientific quantities the experiments purport to measure. Uncovering such discrepancies is beyond the reach of data analysis alone, but we should keep them in mind as we interpret the results.

\subsection{The role of selection bias}

  The RP:P data shows unmistakable signs of selection for statistically significant findings in the original experiments: $91$ of the $100$ results replicated by OSC were statistically significant at the $0.05$ level in the original study and four of the others had ``marginally significant'' $p$-values between $0.05$ and $0.06$. This is due partly to publication bias (that the studies might not have been published, or the results discussed, if the $p$-values had not been significant), but also partly to OSC's method for choosing which results to replicate. Each OSC replication team selected a ``key result'' from the last experiment presented in the original paper, and evidently most teams chose a significant finding as the key result (justifiably so, since positive results usually draw the most attention from journal readers and the outside world). \Cref{fig:pval-dist} shows the empirical distribution of $p$-values from the original and replication studies.
  \begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{ecdf}
    \caption{The empirical distribution of the original and replication $p$-values. Nearly all of the original $p$-values (in red) are smaller than $0.05$.}
  \label{fig:pval-dist}
  \end{figure}

  The resulting selection bias in the original studies leads to many well-known and predictable pathologies, such as systematically inflated effect size estimates, undercoverage of (unadjusted) confidence intervals, and misleading answers from unadjusted meta-analyses. Indeed, most of the phenomena reported by OSC, including the three metrics discussed above, could easily be produced by selection bias alone. This would be true {\em even if there are few false directional claims, all replications are exact, and true effects do not decline}, as illustrated in the following simulation study.

  \begin{example}
    \label{eg:sel-bias}
    Consider a stylized setting where all experiments (both original and replication) have an identical effect size $\theta$, producing an unbiased Gaussian estimate with standard error 1. Assume, however, that we observe only study pairs for which the original study is significant at level $0.05$.

    \Cref{fig:naive-same-dir-func} shows the expected fraction of replication studies which are not statistically significant in the same direction as the corresponding original studies, as a function of effect size $\theta$, along with the true proportion of false directional claims; or type S errors. Even when the true error rate is low, e.g.\ at $\theta = 1$ as shown in \Cref{fig:naive-same-dir-theta1}, the proportion of replications reporting the same directional findings as the original studies can remain low.
    \begin{figure}[htbp]
	    \centering
	    \begin{subfigure}[t]{0.59\hsize}
	      \centering
	      \includegraphics[width=\hsize]{naive-same-dir}
	      \caption{The expected fraction of replications that do not confirm (at level $0.05$) the original directional claim (red), and the proportion of false directional claims in the original studies (blue), as a function of effect size $\theta$. For small $\theta$, the fraction of replications that do not confirm the claims in the original studies may dramatically overestimate the fraction of false original claims.}
	    \label{fig:naive-same-dir-func}
	    \end{subfigure}
	    \hfill
	    \begin{subfigure}[t]{0.39\hsize}
	      \centering
	      \includegraphics[width=\hsize]{naive-same-dir-theta1}
	      \caption{$\theta=1$. The gray region is unobserved. For points in the red region, the replication does not confirm the original directional claim, and for points in the blue region, the original claim is directionally false. The red and blue regions overlap in the purple region.}
	    \label{fig:naive-same-dir-theta1}
	    \end{subfigure}
	    \caption{}
	  \label{fig:naive-same-dir}
	  \end{figure}

    Likewise, we simulate the expected fraction of $95\%$ replication confidence intervals that fail to cover their original point estimates in \Cref{fig:naive-ci-sim} and the expected fraction of effect sizes that decline in \Cref{fig:naive-decline}. In both cases, we see that selection bias is more than sufficient to produce the metrics in RP:P, even in our idealized simulation with exact replications and relatively few type S errors.
    \begin{figure}[htbp]
	    \centering
	    \begin{subfigure}[t]{0.59\hsize}
	      \centering
	      \includegraphics[width=\hsize]{naive-ci-sim}
	      \caption{Expected fraction of original point estimates falling outside the replication confidence interval, as a function of effect size $\theta$. For small $\theta$, the fraction of original point estimates falling outside the replication $95\%$ confidence intervals can easily exceed the RP:P reported metric of $53\%$, even when all replications are perfectly exact.}
	    \label{fig:naive-ci-sim-func}
	    \end{subfigure}
	    \hfill
	    \begin{subfigure}[t]{0.39\hsize}
	      \centering
	      \includegraphics[width=\hsize]{naive-ci-theta05}
	      \caption{$\theta = 0.5$. The gray region is unobserved. For points in the red region, the original point estimate differs from the replication estimate by more than $z_{\alpha/2}$ and hence the original point estimate falls outside in the replication $95\%$ confidence interval.}
	    \label{fig:naive-ci-theta05}
	    \end{subfigure}
	    \caption{}
	  \label{fig:naive-ci-sim}
	  \end{figure}
	  \begin{figure}[htbp]
	    \centering
	    \begin{subfigure}[t]{0.59\hsize}
	      \centering
	      \includegraphics[width=\hsize]{naive-decline}
	      \caption{Expected fraction of effect size point estimates that declined toward zero in replication, as a function of effect size of $\theta$. For small $\theta$, the fraction of effect size estimates declining from original to replication studies can easily exceed the RP:P reported metric of $83\%$, even when there is no decline in the true effect sizes.}
	    \label{fig:naive-decline-func}
	    \end{subfigure}
	    \hfill
	    \begin{subfigure}[t]{0.39\hsize}
	      \centering
	      \includegraphics[width=\hsize]{naive-decline-theta1}
	      \caption{$\theta = 0.5$. The gray region is unobserved. Points in the red region represent declining point estimates in replications. When the original point estimate is positive, a decline is marked by a smaller replication estimate; on the other hand, if the original estimate is negative, a decline is indicated by a larger replication estimate.}
	    \label{fig:naive-ci-theta03}
	    \end{subfigure}
	    \caption{}
	  \label{fig:naive-decline}
	  \end{figure}
  \end{example}

  Because selection bias could, in principle, provide a sufficient explanation for the metrics reported in RP:P, those metrics do not, in and of themselves, provide any evidence of any other problems. In particular, they shed no light on whether the FDR is actually high, or how much the effect sizes shifted, or whether effect sizes tend to decline. Nor do they provide evidence for any competing accounts of the replication crisis, such as QRPs like $p$-hacking, high between-study variability in effect sizes, or systematic biases in the original studies. To discern anything about other explanations, we must adjust for the pervasive effects of selection bias.

  Another good reason to disentangle selection bias from other sources of error is that the former is, in some sense, the most innocuous explanation for the phenomena observed by OSC while the others present much deeper scientific issues. The technical issues of selection bias can be addressed either retrospectively by statistical adjustments \citep[e.g.][]{Duval:2000dg,Hedges:1992eb,Simonsohn:2014ch,Fithian:2014ws,Andrews:2018vh}, or prospectively with more preregistration or larger sample sizes. By contrast, it would be deeply worrying if psychologists were systematically unable to repeat their colleagues' experiments, or if most published claims about effect sizes were directionally incorrect.

\subsection{Formalizing replicability}

  We now introduce a simple formal model for replication studies with selection bias. For study $i=1, \ldots, m$, let $\theta_{i,O}$ and $\theta_{i,R}$ denote the true effect sizes in the original and the replication studies, respectively. Abstracting away experimental design details, assume that each study pair produces two normally distributed effect size estimators $\htheta_{i,O}$ and $\htheta_{i,R}$. Assume additionally that for the study pair to appear in our replication data, $\htheta_{i,O}$ must be statistically significant at level $\alpha=0.05$;\footnote{We relax this assumption in \Cref{sec:methodology}.} then for some significance threshold $c>0$ we have
  \begin{equation}
    \htheta_{i,O} \sim N\left(\theta_{i,O}, \sigma_{i,O}^2\right) 1_{\{|\htheta_{i,O}| > c\}} \qquad\text{ and }\qquad \htheta_{i,R} \sim N\left(\theta_{i,R}, \sigma_{i,R}^2\right),
  \label{eq:trunc-model}
  \end{equation}
  with all estimates assumed to be independent of each other. The indicator $1_{\{|\htheta_{i,O}| > c\}}$ beside the normal distribution in \eqref{eq:trunc-model} means that the distribution of $\htheta_{i,O}$ has been truncated to the event where $|\htheta_{i,O}|>c$ and renormalized so that it integrates to $1$. For the moment, we assume that the variances $\sigma_{i,O}^2$ and $\sigma_{i,R}^2$ are known; in that case $c = z_{0.05 / 2}\, \sigma_{i,O}$. We will relax this assumption in \Cref{sec:methodology}.

  \paragraph{False directional claims} To formalize false directional claims in terms of the parameters of model~\eqref{eq:trunc-model}, we note that a type S error occurs when a statistically significant finding gets the sign of the parameter wrong:
  \[
    H_i^{S,O}:\; \sgn(\theta_{i,O}) \ne \sgn(\htheta_{i,O}), \qquad\text{ where } \sgn(x) =
    \begin{cases}
      +1, & x > 0 \\
      -1, & x < 0 \\
      0, & x = 0
    \end{cases}.
  \]
  Note that $|\htheta_{i,O}|$ is always larger than $c$, so $\sgn(\htheta_{i,O}) \in \{-1,+1\}$. Letting $S_i = \sgn(\htheta_{i,O})$, we can rewrite the hypothesis as
  \[
    H_i^{S,O}:\; S_i\,\cdot\, \theta_{i,O} \le 0.
  \]
  Here $H_i^{S,O}$ is fundamentally data-dependent as it is determined by $S_i$. Nonetheless it is a meaningful hypothesis: when $S_i = +1$, we want to test the null that $\theta_{i,O} \le 0$; otherwise we want to test the null that $\theta_{i,O} \ge 0$. Our strategy is to condition on the value of $S_i$, since the null hypothesis is fixed again once we know $S_i$. We defer the discussion of valid testing of data-dependent hypotheses for now.

  The question of false directional claims, then, boils down to asking how many $H_i^{S,O}$ are true: a multiple testing problem. Our estimand, the proportion of type S errors that occurred, is $V / R$, where $V$ is the number of type S errors and $R$ is the number of ``discoveries,'' i.e.\ rejections. If we classify the hypotheses by whether $H_i^{S,O}$ is true and whether the test for $H_i^{S,O}$ is significant, then $V$ and $R$ correspond to the cell counts in \Cref{tbl:err}.
  \begin{table}[htbp]
    \centering
    \begin{tabular}{lccc}
      \toprule
      Original $p$-value & $H_i^{S,O}$ is true & $H_i^{S,O}$ is false & Total \\
      \midrule
      Significant & $V$ & $*$ & $R$ \\
      Not-significant & $*$ & $*$ & $*$ \\
      Total & $*$ & $*$ & $*$ \\
      \bottomrule
    \end{tabular}
    \caption{Classification of the hypotheses, in the style of \citet{Benjamini:1995cd}. Only $R$ is observed and we wish to infer on $V$.}
  \label{tbl:err}
  \end{table}

  In the multiple testing literature, $V/R$ is called the {\em directional false discovery proportion} (directional FDP, or $\FDPd$), the type S error analog of false discovery proportion \citep[FDP;][]{Benjamini:2000ka}. In addition to an estimate, we also provide an upper confidence bound for the directional FDP in \Cref{sec:methodology}. Both the estimator and the confidence bound are based on a ``$p$-curve'' analysis, i.e.\ an analysis of the distribution of significant $p$-values \citep{Simonsohn:2014fa}. We further modify these methods to evaluate the proposal to lower the statistical significance threshold by \citet{Benjamin:2018gh}.

  Although $\htheta_{i,R}$ is irrelevant to testing $H_i^{S,O}$, it is informative for the closely related question of whether $\htheta_{i,O}$ incorrectly predicts the direction of the effect in a replication study, i.e.
  \[
    H_i^{S,R}:\; S_i \,\cdot\, \theta_{i,R} \le 0.
  \]
  Note that $S_i$ is computed from the original study, so this hypothesis is a measure of external validity as to the (claimed) directions of effects. If an experimental result has external validity, then any directional claim about the true effect should apply not only to the original study, but also to direct replications thereof. We provide analogous methods for multiple testing of the hypotheses $H_i^{S,R}$.

  \paragraph{Effect shift} To assess the effect shift in a specific replication attempt, we can test the hypothesis $H_i^E:\; \theta_{i,O} = \theta_{i,R}$ (an exact replication). As \citet{Anderson:2016gs} noted, ``there is no such thing as exact replication''; nevertheless, exactness serves usefully as an idealized null hypothesis. By inverting a test for $H_i^E$ we can obtain a predictive interval for $\htheta_{i,R}$. Furthermore, by inverting tests for a related hypothesis $H_i^{E,\delta}:\; \theta_{i,O} - \theta_{i,R} = \delta$, we obtain a confidence interval for $\theta_{i,O} - \theta_{i,R}$, the effect shift in study $i$. Our methods explicitly take into account the truncation of $\htheta_{i,O}$.

  \paragraph{Effect size decline} The null hypothesis for effect size decline is closely related to effect shift, and can be formalized as the null hypothesis where the true effect size has declined by no more than a fraction $\rho \in [0, 1]$:
  \[
    H_i^{D,\rho}:\; S_i \,\cdot\, \theta_{i,R} \ge S_i \,\cdot\, (1 - \rho) \theta_{i,O}.
  \]
  If $S_i = +1$ and $\rho=0.2$, for example, rejecting $H_i^{D,\rho}$ amounts to an assertion that $\theta_{i,R} < 0.8 \,\theta_{i,O}$, i.e. the true effect declined by more than $20\%$, or is negative.

  In particular, if $\rho=0$ then $H_i^{D,0}$ is a one-sided version of $H_i^E$, and when $\rho=1$, $H_i^{D,1}$ is equivalent to $H_i^{S,R}$. We can subsequently ask how many of $H_i^{D,\rho}$ are false: another multiple testing problem. We provide two estimators (one overestimate and one underestimate) and confidence interval for the proportion of false $H_i^{D,\rho}$.

\subsection{Data-dependent hypotheses and conditional inference}

  Our hypotheses above, $H_i^{S,O}$, $H_i^{S,R}$ and $H_i^{D,\rho}$, are all innately data-dependent. While data-dependent hypotheses may at first sound unusual, they are commonplace in practice, for example when pilot studies are performed to generate hypotheses that are tested later on with fresh data. There is no inherent conceptual problem with testing these data-dependent hypotheses: intuitively, we understand that the test remains valid because the type I error rate is controlled for whatever hypothesis is selected, conditional on that hypothesis having been selected.

  Conditional inference is well-established in the statistical literature as a means of constructing valid confidence intervals for parameters that were selected in a data-dependent way \citep[e.g.][]{Sampson:2005,Zollner:2007,Weinstein:2013,Yekutieli:2012}. \citet{Fithian:2014ws} generalized the intuition about pilot studies to argue that a test of a data-dependent hypothesis is valid, so long as the type I error rate is controlled conditioned on the portion of the data that generated the hypothesis. For our hypotheses here, $S_i$ is the part of the data that determines the hypothesis: in effect, we can imagine ourselves in the position of having observed the signs of all the original estimators, but knowing nothing else about the data. At that stage, it is valid to formulate a hypothesis that depends on $S_i$, and plan to test it using the still-unobserved data: namely, $|\htheta_{i,O}|$ and $\htheta_{i,R}$.

  After conditioning on $S_i$, each hypothesis discussed above amounts to testing a fixed linear hypotheses about $(\theta_{i,R}, \theta_{i,O})$, the natural parameter of the truncated bivariate normal model~\eqref{eq:trunc-model}; as a result, they are all amenable to post-selection inference using the selective $z$-test built on the work of \citet{Lee:2016fv}. \Cref{sec:methodology} discusses the methodology in detail.

\subsection{Related work}

  There has been much commentary on how to define replicability for scientific experiments. \citet{Valentine:2011ga} pointed out that the definition should depend on the scientific context. For example, sometimes one may wish to test the robustness of conclusions to subpopulation differences, but in other times, to changes in experimental conditions. \citet{Goodman:2016bo} expanded on this, and gave a few useful definitions for what replicability is, such as {\em methods reproducibility}, {\em results reproducibility}, {\em inferential reproducibility}, etc., but stopped short of an operational statistical criterion for replicability. False directional claims and effect shift can be loosely interpreted as inferential and results reproducibility, respectively.

  Operationally, \citet{Valentine:2011ga} and \citet{Nosek:2017ei} proposed the metrics used in RP:P and \citet{Camerer:2018de}, a similar replication effort in experimental economics. These metrics however suffer the shortcomings discussed earlier, in that they do not answer a concrete statistical question and cannot disentangle selection bias from other explanations.

  In this article, our definitions of replicability are inspired primarily by the statistical literature on multiple testing and meta-analysis, such as the estimator in \citet{Storey:2002vj}, the FDP and directional FDP from \citet{Benjamini:2000ka,Benjamini:2005bv}, and the partial conjunction testing framework of \citet{Heller:2007,Benjamini:2008kj}. Related error rates have also been estimated before: \citet{Jager:2013dq} have modeled the $p$-value distributions under alternatives and the selection for statistical significance to estimate the FDR in the medical literature, accompanied by useful discussions from \citet{Gelman:2013ep,Goodman:2013kj,Ioannidis:2013fz}; in addition, \citet{Camerer:2018de} used Bayesian methods to estimate the false positive rate, instead of the FDR, for published social science results in {\em Nature} and {\em Science}.

  Furthermore, there are many past efforts to model and quantify selection bias, specifically using the RP:P dataset. For instance, \citet{Johnson:2017gu} considered a publication bias model where the probability of publication is a step function of the $p$-value, which is generalized nonparametrically in \citet{Andrews:2018vh}. The two analyses estimated that a statistically significant result was $200$ \citep{Johnson:2017gu} or $30$ \citep{Andrews:2018vh} times as likely to be published as a statistically insignificant one.

  Adjusting for selection, \citet{vanAert:2017,vanAert:2018} have combined the evidences from both the original and replication experiments to provide estimates for the effect sizes. Specifically with a truncated Gaussian model, \citet{Etz:2016gx} have also analyzed the RP:P dataset from a Bayesian perspective, and investigated the discrepancies between the original and replication studies. Our analysis provides a complementary point of view with frequentist hypothesis testing without any prior on the effect sizes, with the help of recent advances in post-selection inference, including primarily the selective $z$-test framework of \citet{Lee:2016fv}.

\subsection{Outline}

  \Cref{sec:methodology} details the methodology and assumptions used in this analysis, and is somewhat technical. \Cref{sec:analysis} applies the developed methodology to the RP:P dataset, summarizes and interprets the results. \Cref{sec:discussion} concludes.

\section{Methodology}
\label{sec:methodology}

  In this section we will construct an estimator for directional FDP, a test for the effect shift in replication $i$ and an estimator for the proportion of effect sizes that declined. We also use $X \gest Y$ to denote that $X$ is stochastically larger than $Y$. The index $i$ is suppressed when there is no risk of ambiguity.

  Since we need a well-defined notion of direction to consider the proportion of false directional claims, we restrict our attention to univariate tests, namely $z$-, $t$-, $F(1, \cdot)$-tests or correlations. Thus, studies that are not univariate or have $p$-values greater than $\ao = 0.05$ are discarded: our estimates and analyses below consider only the $m = 68$ remaining studies with univariate structure and conventionally significant original $p$-values.

\subsection{Selection bias model}
  Model~\eqref{eq:trunc-model} assumes that results are only published if they achieved statistical significance at some conventional threshold level $\ao$, which is $0.05$ in our data. While this assumption is not literally true in the case of RP:P since some original $p$-values are above $0.05$, we note that the model can be relaxed to the following milder assumption:
  \begin{assumption}
    \label{ass:sig-enough}
    $p_O < \ao$ is ``significant enough'': that is, not all results with significant $p$-values are necessarily published, but a result with $p_O < \ao$ would have been equally likely to be published (or selected for replication), had the $p$-value taken on some other statistically significant value.
  \end{assumption}

  If \Cref{ass:sig-enough} holds, then we can model the original test statistics as following their theoretical distribution, truncated to the event where the corresponding $p$-values are below $\ao$, as in Model~\ref{eq:trunc-model}.

  Note that \Cref{ass:sig-enough} contemplates a fairly straightforward mechanism for selection on statistical significance, which may not be adequate to describe the effects of more complex and difficult-to-model QRPs. In particular, $p$-hacking --- the iterative tweaking of an analysis until the $p$-value drops below the researcher's desired significance level $\ao$ --- is commonly suspected to produce a pileup of $p$-values just below the significance threshold \citep[see e.g.][]{Simonsohn:2014fa}. Because $p$-hacking is such a vaguely defined practice, it is unclear how we might incorporate it into our model, but in any case there is no evidence of a pileup just below $0.05$ in the original RP:P studies (see \Cref{fig:fdp-original}).

\subsection{False directional claims}

  We will adapt the method in \citet{Storey:2002vj} to estimate the directional FDP while accounting for selection bias. Furthermore, if we believe the chosen studies are representative of the publications in the journal or discipline \citep[e.g.][]{Stroebe:2016dj}, then this estimator can also be regarded as an estimator for the journal-wide or discipline-wide directional false discovery rate (FDR\textsubscript{dir}), the expectation of the directional FDP \citep{Benjamini:2005bv}.

  \paragraph{Adjusting for selection bias} While dividing a post-selection $p$-value by $\ao$ intuitively adjusts for selection, it is not immediately valid when the null is one-sided with a true effect not on the boundary. We demonstrate below that this adjustment typically remains valid even in this case.

  Recall that a valid $p$-value is a random variable that is stochastically larger than $\Uniform[0, 1]$ (i.e.\ superuniform) under the null hypothesis. If we only observe the original $p$-value when it is significant, it is not superuniform after selection under $H^{S,O}$, and it is therefore not valid for testing the hypothesis of a false directional claim. To adjust these $p$-values for selection, we follow the principle in \citet{Fithian:2014ws} by conditioning on the event that the $p$-values are selected, and also on the variable $S = \sgn(\htheta_O)$ which determines the hypothesis $H^{S,O}$ that we test. We consider two cases: when the original study is a one-sided test and when it is a two-sided test. As we will see, the adjustment in either case is to divide by $\ao$.

  First we consider the case where the original study was a one-sided test. Assume $p_O$ is a $p$-value for a test of the hypothesis $H_0:\; \theta_O \le 0$, in which case $S = +1$ deterministically (the opposite case with $H_0:\; \theta_O \ge 0$, and $S = -1$ deterministically, is directly analogous). Suppose $p_O$ is the original $p$-value, which we observe only when it is significant at the conventional threshold, i.e. when $p_O < \ao$. Under mild assumptions satisfied by both $z$-tests and $t$-tests,\footnote{namely, that the test statistic has monotone likelihood ratio in the parameter} $p_O \gest \Uniform[0, \ao]$ under $H^{S,O}$, in which case $p_O/\ao \gest \Uniform[0,1]$.

  Next we consider the case where $p_O$ is a $p$-value for a two-sided test of $H_0:\; \theta_O = 0$, and where $S = +1$ (the case with $S = -1$ is analogous). If $p_O^+$ was the original one-sided $p$-value for $H_0:\; \theta_O\le 0$, then $p_O = 2p_O^+$ when $S=+1$ ($p_O = 2 - 2p_O^+$ if $S = -1$). In our truncated model, under the same assumptions as above and conditional on $S = +1$, $p_O^+ \gest \Uniform[0, \ao/2]$ and therefore $p_O/\ao = 2p_O^+/\ao \gest \Uniform[0, 1]$ under $H^{S,O}$. We write $p_O'=p_O/\ao$ for the adjusted $p$-value.

  \paragraph{Inference on FDP: estimate and upper confidence bound} Using the adjusted original $p$-values, we can estimate the directional FDP in the original studies. Recall from \Cref{tbl:err} that
  \begin{align*}
    R &= \#\{p_{i,O} \le \ao\} = m,\\
    V &= \#\{p_{i,O} \le \ao \text{ and } H_i^{S,O} \text{ is true}\}.
  \end{align*}
  Since all of the studies were deemed discoveries, $R=m$ is the total number of studies here. \Cref{tbl:err-fdp} classifies the $m$ conventionally significant studies according to whether $H_i^{S,O}$ is true and whether the adjusted $p$-value is larger than some fixed value $\lambda$ in $(0,1)$, e.g.\ $\lambda = 0.5$.
  \begin{table}[htbp]
    \centering
    \begin{tabular}{lccc}
      \toprule
      Adjusted $p$-value & $H_i^{S,O}$ is true & $H_i^{S,O}$ is false & Total \\
      \midrule
      $p_{i,O}' < \lambda$ & $*$ & $*$ & $*$ \\
      $p_{i,O}' \ge \lambda$ & $U$ & $*$ & $B$ \\
      Total & $V$ & $*$ & $R = m$ \\
      \bottomrule
    \end{tabular}
    \caption{Classification of the $R=m$ significant original studies. Here only $R$ and $B$ are observed, and we wish to infer on $V$.}
  \label{tbl:err-fdp}
  \end{table}

  Note that $B = \#\{\lambda\ao \le p_{i,O} < \ao\}$ from \Cref{tbl:err-fdp} is observable, while $V$ and $U$ are not. Under the one-sided null, the $p$-value is superuniform, and so 
  \begin{equation}
    B \gest U \gest \Binomial(V, 1-\lambda).
  \label{eq:Bgest}
  \end{equation}
  As a result, $\EE[B] \ge (1-\lambda)V$ and a conservative (upwardly biased) estimator of the directional FDP is
  \[
    \hFDPd = \frac{B}{(1 - \lambda)R}.
  \]
  This estimate is conservative in the sense that it overestimates the type I error, and is equivalent to the estimator $\hat{\pi}_0$ of the true null proportion in \citet{Storey:2002vj}. Using $\lambda = 0.5$ and $\ao = 0.05$, the estimate boils down to
  \[
    \hFDPd = \frac{2}{m} \cdot \#\{0.025 \le p_{i,O} < 0.05\}.
  \]

  While the above is formally an estimator for the number of directional errors, it can be interpreted practically as an estimate of the fraction of directional claims where {\em either} the direction is wrong {\em or} the effect has a negligible magnitude, cf.\ type M error from \citet{Gelman:2014cd}. This is because $p$-values whose effect sizes are very close to zero are nearly uniform and contribute to our estimator similarly as if the true effect were exactly zero.

  Additionally, we can exploit \eqref{eq:Bgest} to obtain an upper confidence bound for the directional FDP, by testing the hypothesis $H_0:\; V \ge v_0$, a partial conjunction hypothesis investigated in \citet{Heller:2007}. Here we combine only the coarse information of whether each $p$-value is greater than $\lambda$,\footnote{More precisely, we count number of $p$-values that are greater than $\lambda$ and consider its distribution under the partial conjunction null hypothesis} and reject for small values of $B$. We can compute the largest $v_0$ such that the test still accepts, which gives an upper confidence bound of $V$. Dividing this bound by $R$ gives an upper confidence bound for the directional FDP.

  \paragraph{Directional FDP at smaller thresholds} One proposal to address the replicability crisis is to lower the conventional significance threshold from $\ao=0.05$ to some smaller value $\alpha$, such as $0.005$ \citep{Benjamin:2018gh}. As suggested by \citet{Goodman:2013kj}, an empirical method to evaluate the hypothetical scenario with a smaller threshold can be helpful. We now discuss methods for inference on the directional FDP for those studies with $p_O < \alpha < \ao$, based on comparing the number of adjusted $p$-values below $\alpha$ with the number above $\lambda\ao$, for some $\lambda > \alpha/\ao$. We call this method the {\em external comparison method} in contrast to the earlier {\em internal comparison method}. This method will be less conservative as we are not constrained to only using the $p$-values in $[0, \alpha)$.

  Let $N \le m$ denote the total number of original $p$-values in $[0,\alpha) \cup [\lambda\ao, \ao)$ (or equivalently, the number of adjusted $p$-values in $[0,\alpha') \cup [\lambda, 1)$ for $\alpha' = \alpha/\ao$). \Cref{tbl:big-small} classifies these $N$ studies according to whether $H_i^{S,O}$ is true and whether the adjusted $p$-value is larger than $\lambda$ or smaller than $\alpha'$. The numbers of false directional claims and all directional claims under the hypothetical threshold are $V_\alpha$ and $R_\alpha$, respectively. Auxiliary counts, $T_\alpha$ and $W$, are defined according to \Cref{tbl:big-small} as well. The directional FDP, $V_\alpha / R_\alpha$, remains as our quantity of interest.

  \begin{table}[htbp]
    \centering
    \begin{tabular}{lccc}
      \toprule
      Adjusted $p$-value & $H_i^{S,O}$ is true & $H_i^{S,O}$ is false & Total \\
      \midrule
      Small ($p_{i,O}' < \alpha'$) & $V_\alpha$ & $T_\alpha$ & $R_\alpha$ \\
      Big ($p_{i,O}' \ge \lambda$) & $U$ & $W$ & $B$ \\
      Total & $N_0$ & $*$ & $N$ \\
      \bottomrule
    \end{tabular}
    \caption{Classification of the $N \le m$ original studies with adjusted $p$-values in $[0, \alpha'] \cup [\lambda, 1]$. Only $R_\alpha$, $B$ and $N$ are observed. Auxiliary unobserved quantities, $N_0$, $T_\alpha$ and $R_\alpha$, are defined accordingly. Our goal is to infer on $V_\alpha$.}
    \label{tbl:big-small}
  \end{table}

  Our method is inspired by the following stochastic inequality.
  \begin{lemma}
    Conditional on $N$, $T_\alpha$ and $W$, we have
    \begin{equation}
      B \mid N, T_\alpha, W \gest \Binomial(N - T_\alpha, \beta).
    \label{eq:B-NTW}
    \end{equation}
  \end{lemma}
  \begin{proof}
    All adjusted $p$-values are independent, and are either small ($p \le \alpha'$) or big ($p \ge \lambda$). The adjusted $p$-values corresponding to a true null are big with probability at least $\beta = \frac{1 - \lambda}{1 - \lambda + \alpha'}$. We proceed to condition on $T_\alpha$ and $W$, so they are now considered deterministic. So the total number of big adjusted $p$-values, $B$, satisfies
    \[
      B = U + W \gest \Binomial(N-N_0, \beta) + W \gest \Binomial(N-T_\alpha, \beta).
    \]
  \end{proof}

  With \eqref{eq:B-NTW}, we can estimate $N - T_\alpha$ conservatively with $B / \beta$. Since $V_\alpha  = N - T_\alpha - B$, a reasonable estimator for the directional FDP is
  \[
    \hFDPd = \frac{1 - \beta}{\beta} \cdot \frac{B}{R_\alpha}.
  \]
  Furthermore \eqref{eq:B-NTW} gives us a $95\%$ upper confidence bound for the directional FDP:
  \[
    \FDPd^* = \frac{Q - B}{R_\alpha}, \qquad\text{where } Q = \max\{q: \PP[\Binomial(q, \beta) \ge B] \ge 0.95\}.
  \]

  \begin{proposition}
    The expectation of $\hFDPd$ is at least the expectation of the true directional FDP, and $\FDPd^*$ is greater than the true directional FDP, with probability at least $95\%$.
    \label{prop:prereg-test}
  \end{proposition}
  \begin{proof}
    For the estimator, we start by taking the expectation of $\hFDPd - \FDPd$, conditional on $N$, $T_\alpha$ and $W$:
    \begin{align}
      \EE[\hFDPd - \FDPd \mid N, T_\alpha, W] &= \EE\left[\frac{\frac{1-\beta}{\beta} B - V_\alpha}{R_\alpha} \,\middle|\, N, T_\alpha, W\right] \nonumber \\
      &\ge \EE\left[\frac{\frac{1-\beta}{\beta} (N_0 - V_\alpha) - V_\alpha}{V_\alpha + T_\alpha} \,\middle|\, N, T_\alpha, W\right] \nonumber \\
      &= \EE\left[\frac{(1-\beta) N_0 - V_\alpha}{\beta (V_\alpha + T_\alpha)} \,\middle|\, N, T_\alpha, W\right] \nonumber \\
      &\ge \frac{(1-\beta) N_0 - \EE[V_\alpha \mid N, T_\alpha, W]}{\beta (\EE[V_\alpha \mid N, T_\alpha, W] + T_\alpha)} \label{eq:jensen} \\
      &\ge 0 \label{eq:binom-ineq},
    \end{align}
    where \eqref{eq:jensen} follows from applying Jensen's inequality to the convex function $f(x) = \frac{(1-\beta) N_0 - x}{\beta(x + T_\alpha)}$, and \eqref{eq:binom-ineq} follows from $V_\alpha \mid N, T_\alpha, W \lest \Binomial(N_0, 1-\beta)$. Taking expectation on both sides completes the proof.

    For $\FDPd^*$, we can directly compute the probability that it is greater than $\FDPd$, conditional on $N$, $T_\alpha$ and $W$:
    \begin{align*}
      \PP[\FDPd^* \ge \FDPd \mid N, T_\alpha, W] &= \PP\left[\frac{Q - B}{R_\alpha} \ge \frac{V_\alpha}{R_\alpha} \,\middle|\, N, T_\alpha, W\right] \\
      &= \PP[Q \ge B + V_\alpha \mid N, T_\alpha, W] \\
      &= \PP[Q \ge N - T_\alpha \mid N, T_\alpha, W] \\
      &\ge 0.95,
    \end{align*}
    from the construction of $Q$. Taking expectation on both sides hence yields the desired marginal coverage.
  \end{proof}

  \begin{remark}
    This proof of conservativeness actually shows something stronger than marginal guarantees: the estimator and confidence upper bound are both conservative conditionally, even when we condition on the signs $S_i$.
  \end{remark}

  \paragraph{Methods using replication $p$-values} As mentioned in \Cref{sec:intro}, we can use the replication $p$-values in lieu of the adjusted original $p$-values above, providing an estimate and confidence bound for the frequency of when the $\htheta_O$ incorrectly predicts the replication effect direction. While this approach requires potentially costly replications in future applications, it provides valuable additional information. In particular, the replication $p$-values are more likely to be free of QRPs or $p$-hacking that may violate our assumption that adjusted $p$-values are superuniform under the null, providing more robust evidence regarding replicability. The corresponding estimator for unadjusted replication $p$-values with $\lambda= 0.5$ is 
  \[
    \hFDPd = \frac{2}{m} \cdot \#\{p_{i,R} \ge 0.5\}.
  \]

\subsection{Effect shift}

  We will derive a test for the hypothesis $H^E: \theta_O = \theta_R$ at level $0.05$. Our test is based on a normal distribution, so we start by demonstrating that the effect size estimates of the univariate studies can be reasonably modeled by our truncated bivariate normal distribution in model~\eqref{eq:trunc-model}. We classify these studies into two categories and provide a rough rationale in our definition of effect size in each category:
  \begin{inlinelist}
    \item $t$-tests and $F(1, \cdot)$ ANOVAs, where all independent variables are categorical; and,
    \item correlations and regressions, where one or more independent variables are continuous.
  \end{inlinelist}

  For a $t$-test or $F(1, \cdot)$ ANOVA, we can define the effect size as the noncentrality parameter, scaled for cell sizes. In other words, the $t$-statistic is distributed as $T \sim t_{df}(k\theta)$, for some real constant $k$ chosen based on the study design. For example, $k = \sqrt{n}$ for a one-sample $t$-test. When $df$ is sufficiently large, the $t$-statistic is approximated well by a $z$-statistic, and distributed approximately as
  \[
    T \sim N(k\theta, 1).
  \]
  For our analysis, we consider studies where the original and replication degrees of freedom are at least $30$.\footnote{The choice of $30$ complies with the analysis in \citet{Andrews:2018vh}. Further discussion on the approximation in available in the supplement.}

  For a (partial) correlation coefficient estimate, $R$, we can apply Fisher transformation \citeyearpar{Fisher:1921vq,Fisher:1924ve} to convert it into a $z$-statistic, which approximately follows
  \[
    \sqrt{n-3-p} \tanh^{-1}(R) \sim N(\sqrt{n-3-p}\,\theta, 1),
  \]
  where $p$ is the number of controlled covariates and $\theta$ is a quantity that can be taken as the effect size.

  In either case, the test statistic in $46$ studies can be transformed to an approximate $z$-score $Z \sim N(k \theta, 1)$ for some real constant $k$. Additional considerations in certain studies are detailed in the supplement.

  \paragraph{Adjusting for selection bias} We turn next to address the issue of post-selection inference. Again, we condition on the event where the $z$-scores are observed, but we do not need to condition on $S$ as the hypothesis $H^E$ is no longer random. Since the statistic is only observed if it is statistically significant, the original and replication $z$-statistics follow a truncated bivariate normal joint distribution:
  \[
    \begin{bmatrix}
      Z_O \\ Z_R
    \end{bmatrix} \sim N\left(\begin{bmatrix}
      k_O \theta_O \\ k_R \theta_R
    \end{bmatrix}, \begin{bmatrix}
      1 & 0 \\ 0 & 1
    \end{bmatrix}\right) 1_{\{Z_O \in A\}}.
  \]
  Here $A$ is the selection event, which contains the statistically significant values of $Z_O$. We are interested in testing $H^E: \theta_O = \theta_R$ and more generally the null hypothesis $H^{E,\delta}: \theta_O - \theta_R = \delta$, which can be inverted to yield a confidence interval.

  We cast this as a more general testing problem here to benefit later derivations on effect decline. Suppose we have a truncated bivariate distribution
  \[
    Z = \begin{bmatrix}
      Z_1 \\ Z_2
    \end{bmatrix} \sim N\left(\mu, \begin{bmatrix}
      1 & 0 \\ 0 & 1
    \end{bmatrix}\right) 1_{\{Z_1 \in A\}}, \quad \text{where } \mu = \begin{bmatrix}
      \mu_1 \\ \mu_2
    \end{bmatrix},
  \]
  and we want to test $\eta' \mu = \delta$ for some constant vector $\eta = (\eta_1, \eta_2)$ with $\eta_1 > 0$. Test for $H^E$ and $H^{E,\delta}$ are special cases where $\eta = (1/k_O, -1/k_R)$.

  We can perform this general testing problem with the {\em selective $z$-test}, based on the framework in \citet{Lee:2016fv}.

  \begin{definition}[Selective $z$-test]
  \label{def:sel-gauss}
    Let $\eta_\perp = (\eta_2, -\eta_1)$, $D = \eta' Z$ and $M = \eta_\perp' Z$. We now consider $M$ as a constant and test $\eta' \mu = \delta$ using the test statistic $D$ against the null distribution
    \[
      N(\delta, \|\eta\|^2) 1_{\left\{D \in \frac{\|\eta\|^2 A - \eta_2 M}{\eta_1}\right\}}.
    \]
    Specifically, we reject $\eta' \mu = \delta$ when $D$ is below the $\frac{0.05}{2}$-quantile or over the $(1 - \frac{0.05}{2})$-quantile of this null distribution.
  \end{definition}

  We proceed to show that this is a valid test by construction.

  \begin{proposition}
  \label{prop:sel-gauss}
    The selective $z$-test defined in \Cref{def:sel-gauss} has level $0.05$.
  \end{proposition}

  \begin{proof}
    Leveraging the fact that $\eta' \eta_\perp = 0$, we reparametrize the joint distribution of $(Z_1, Z_2)$ under the null such that $\delta$ is a parameter, i.e.
    \[
      \begin{bmatrix} D \\ M \end{bmatrix} =
      \begin{bmatrix} \eta' \mu \\ \eta_\perp' \mu \end{bmatrix}
      \sim N\left(
      \begin{bmatrix} \delta \\ \eta_\perp' \mu \end{bmatrix},
      \begin{bmatrix}
        \|\eta\|^2 & 0 \\
        0 & \|\eta\|^2
      \end{bmatrix}\right) 1_{\{Z_1 \in A\}}.
    \]
    In particular, the event $Z_1 \in A$ can be rewritten as
    \[
      D \in \frac{\|\eta\|^2 A - \eta_2 M}{\eta_1}.
    \]
    And so the distribution of $D$ conditional on $M$ under $H_0^\delta$ is a truncated Gaussian distribution,
    \[
      [D \mid M] \sim N\left(\delta, \|\eta\|^2\right) 1_{\left\{D \in \frac{\|\eta\|^2 A - \eta_2 M}{\eta_1}\right\}}
    \]
    and we obtain a valid test by rejecting when $D$ is smaller than the $\frac{0.05}{2}$-quantile or larger than the $\left(1 - \frac{0.05}{2}\right)$-quantile.
  \end{proof}

  The construction above is represented graphically in \Cref{fig:sel-gauss}, in the style of \citet{Lee:2016fv}. We can represent the observation $(Z_1, Z_2)$ as a point in $\mathbb{R}^2$. Conditioning on $M$ is equivalent to conditioning on $M / \|\eta_\perp\|$, which means we are now considering the conditional distribution on the truncated line $\ell$. The test statistic $D$, or equivalently $D / \|\eta\|$, indicates the position on $\ell$. Under the null that $\eta' \mu  = \delta$, the conditional distribution on $\ell$ is known and a valid $p$-value can be obtained, yielding the selective $z$-test.
  \begin{figure}[htbp]
    \centering
    \begin{tikzpicture}
    \fill[mid-blue] (-4, -3) -- (-4, 3) -- (-1, 3) -- (-1, -3) -- cycle;
    \fill[mid-blue] (4, -3) -- (4, 3) -- (1, 3) -- (1, -3) -- cycle;
    \draw[thick, ->] (0, -3.25) -- (0, 3.25) node[above] {$z_2$};
    \draw[thick, ->] (-4.25, 0) -- (4.25, 0) node[right] {$z_1$};
    \draw[dashed] (-1, -3) -- (-1, 3);
    \draw[dashed] (1, -3) -- (1, 3);
    \fill (2, 0.5) circle(2pt) node[above right] {$(Z_1, Z_2)$};
    \draw[thick, ->] (0, 0) -- (2, -1) node[below right] {$\eta$};

    \draw[thick, <->] (0, 0) -- (0.6, 1.2) node[midway, left] {$M / \|\eta_\perp\|$};
    \draw[thick] (-3, 3) -- (-1, 2);
    \draw[thick, dashed] (-1, 2) -- (1, 1);
    \draw[thick] (1, 1) -- (4, -0.5) node[right] {$\ell$};

    \draw[thick, <->] (0.7, 1.4) -- (2.1, 0.7) node[midway, above] {$D / \|\eta\|$};
    \end{tikzpicture}
    \caption{Graphical representation of the selective $z$-test. The observation $(Z_1, Z_2)$ is a point and the truncation on $Z_1$ means that the shaded area is the support of the joint distribution $(Z_1, Z_2)$. Conditioning on $M$ is the same as conditioning on $M / \|\eta_\perp\|$, so we now consider the conditional distribution on the truncated line $\ell$. The test statistic $D$ indicates the position on $\ell$. Under the null $H^{E,\delta}: \theta_1 - \theta_2 = \delta$, the conditional distribution on $\ell$ is known and a valid $p$-value can be obtained, yielding the selective $z$-test.}
  \label{fig:sel-gauss}
  \end{figure}

  \begin{remark}
    It is not necessary to use $\frac{0.05}{2}$- and $(1 - \frac{0.05}{2})$-quantiles of the null distribution, as long as the desired significance level is achieved under the null distribution. For example, a uniformly most powerful unbiased test can be used in lieu of a test with equal tail cutoffs. Furthermore, if we are interested in a one-sided hypothesis, e.g.\ $\eta' \mu \le 0$, we can reject on one tail only. This will be particularly useful for derivations about effect decline later.
  \end{remark}

  \paragraph{Interval estimation} Given a valid test $\phi(Z_O, Z_R)$ for testing $H^{E,\delta}: \theta_O - \theta_R = \delta$, we can obtain two intervals: a predictive interval for the replication effect size estimate, and a confidence interval for effect shifts.

  Under the null hypothesis $H^E: \theta_O = \theta_R$, $\PP[\phi(Z_O, Z_R) \text{ rejects}] = 0.05$, or equivalently,
  \[
    \PP[\{z_R: \phi(Z_O, z_R) \text{ accepts}\} \ni Z_R] = 0.95.
  \]
  Hence $\{z_R: \phi(Z_O, z_R) \text{ accepts}\}$ is a predictive interval for $Z_R$, which translates to a predictive interval for the point estimate $\htheta_R$ of the replication effect size.

  By the duality of hypothesis testing and confidence set, the set
  \[
    \{\delta: H^{E,\delta} \text{ is rejected}\}
  \]
  covers the difference of the original and replication effect sizes with probability $95\%$.

\subsection{Effect decline}

  We will estimate the proportion of effect sizes that declined by at least a fraction of $\rho$. Our procedure consists of two parts:
  \begin{inlinelist}
    \item for each study $i$, test and produce a $p$-value for the hypothesis $H_i^{D,\rho}$, and
    \item adapt the method for the directional FDP to estimate the proportion of $H_i^{D,\rho}$ that are false.
  \end{inlinelist}

  \paragraph{Adjusting for selection bias} As with the exactness test, we condition not only on the event where the $z$-scores are observed, but also on $S = \sgn(\htheta_O)$ as our hypothesis $H^{D,\rho}$ is determined by this random variable. In other words, we consider the $z$-statistic $Z_O$ to be drawn from the set $A_+$, where $A$ is the selection event from our test for effect shift and
  \[
    A_+ = A \cap \RR_+ = \{z_O: z_O \text{ is statistically significant}\} \cap \RR_+.
  \]
  Putting $Z_O$ and $Z_R$ together, they follow a truncated bivariate normal joint distribution:
  \[
    \begin{bmatrix}
      Z_O \\ Z_R
    \end{bmatrix} \sim N\left(\begin{bmatrix}
      k_O \theta_O \\ k_R \theta_R
    \end{bmatrix}, \begin{bmatrix}
      1 & 0 \\ 0 & 1
    \end{bmatrix}\right) 1_{\{Z_O \in A_+\}}.
  \]
  By convention RP:P chose $\htheta_O > 0$ so the hypothesis $H^{D,\rho}$ reduces to $\theta_{i,R} \ge (1-\rho) \theta_{i,O}$, or equivalently $\theta_{i,R} - (1-\rho) \theta_{i,O} \ge 0$. This can be tested using the selective $z$-test with $\eta = (1/k_O, -1/(1-\rho)k_R)$ and rejecting on one tail only.

  \paragraph{Inference on effect decline: estimates and confidence bounds} With the resulting $p$-values, our earlier methods on directional FDP can provide an overestimate and a upper confidence bound for the proportion of true $H^{D,\rho}$. Subtracting these from $1$ yields an underestimate and a lower confidence bound for the proportion of false $H^{D,\rho}$. On the other hand, by considering the complement of the hypothesis $H^{D,\rho}$, we can also provide an overestimate and an upper confidence bound for the proportion of false $H^{D,\rho}$. These estimators and bounds together provide an overestimate, an underestimate and a $90\%$ confidence interval for the proportion of effect sizes that at least declined by a fraction of $\rho$.

\section{Re-analysis of RP:P}
\label{sec:analysis}

\subsection{False directional claims}

  We implemented our method with $\lambda = 0.5$ to estimate the number of one-sided nulls and the directional FDP.\footnote{Choosing $\lambda = 0.5$ follows the convention in the multiple testing literature for a bias-variance trade off: if $\lambda$ is too small, many true discoveries are counted as false; if $\lambda$ is too big, the estimator can have large variance.} The adjusted original $p$-values and replication $p$-values are given in \Cref{fig:fdp-original,fig:fdp-replication} respectively. Using the original $p$-values, we estimate that $22$ of the $68$ ($32\%$) original directional claims are false, with a $95\%$ upper confidence bound of $47\%$. Using the replication $p$-values, we estimate that $32$ of the $68$ ($47\%$) original directional claims incorrectly predict the direction of the replication effect, with a $95\%$ upper confidence bound of $63\%$. In particular both of our FDP estimates are much lower than the $64\%$ which could be suggested by a naive reading of RP:P \citep[e.g.][]{Baker:2015kd}. These numbers are summarized again in \Cref{tbl:fdp-sim} later. Furthermore, while we can compute a lower confidence bound, it will always be $0\%$ as the data is obviously consistent with many null hypotheses being slightly false.
  \begin{figure}[htbp]
    \centering
    \begin{subfigure}[t]{0.49\hsize}
      \centering
      \includegraphics[width=\hsize]{fdp-original}
      \caption{Histogram of the adjusted original $p$-values.}
    \label{fig:fdp-original}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.49\hsize}
      \centering
      \includegraphics[width=\hsize]{fdp-replication}
      \caption{Histogram of the replication $p$-values.}
    \label{fig:fdp-replication}
    \end{subfigure}
    \caption{Histograms of $p$-values. We estimate the expected number of true nulls in each bin by the method from \citet{Storey:2002vj}, shown by the horizontal red line. A net excess of $p$-values above this line means false directional claims.}
  \end{figure}

  We proceeded to evaluate the proposal to reduce the statistical significance threshold \citep{Benjamin:2018gh}. We considered three candidates for the new threshold, $0.001$, $0.005$ and $0.01$, using the external comparison method. The directional FDP estimates and upper confidence bounds are given in \Cref{tbl:fdp-sim}.
  \begin{table}[htbp]
    \centering
    \begin{tabular}{rr@{\hspace*{0.25em}}r@{}lr@{\hspace*{0.25em}}r@{}lr@{\hspace*{0.25em}}rr@{\hspace*{0.25em}}r}
      \toprule
      \multirow{2}{*}{\raisebox{-\heavyrulewidth}{$\alpha$}} & \multicolumn{6}{c}{Adjusted original} & \multicolumn{4}{c}{Replication} \\
      \cmidrule(lr){2-7} \cmidrule(lr){8-11}
      & \multicolumn{3}{c}{Est.} & \multicolumn{3}{c}{U.C.B.} & \multicolumn{2}{c}{Est.} & \multicolumn{2}{c}{U.C.B.} \\
      \midrule
      $0.001$ & $0.4 / 22 =$&$2\%$&\textdagger & $2 / 22 =$&$9\%$&\textdagger & $6 / 22 =$&$27\%$ & $12 / 22 =$&$55\%$ \\
      $0.005$ & $2.2 / 33 =$&$7\%$&\textdagger & $6 / 33 =$&$18\%$&\textdagger & $12 / 33 =$&$36\%$ & $20 / 33 =$&$61\%$ \\
      $0.01$ & $4.4 / 41 =$&$11\%$&\textdagger & $9 / 41 =$&$22\%$&\textdagger & $16 / 41 =$&$39\%$ & $25 / 41 =$&$61\%$ \\
      $0.05$ & $22 / 68 =$&$32\%$ && $32 / 68 =$&$47\%$ && $32 / 68 =$&$47\%$ & $43 / 68 =$&$63\%$ \\
      \bottomrule
    \end{tabular}
    \caption{The directional FDP estimates and $95\%$ upper confidence bounds, using the adjusted original and replication $p$-values. The statistical significance level is $\alpha$. The external comparison method was used for computing the directional FDP estimates and the upper confidence bounds marked with daggers(\textdagger) above, as information of $p$-values between $\alpha$ and $0.05$ can improve the precision. The estimates and upper confidence bounds in the ``Replication'' column are relatively noisy due to the small number of $p$-values below the stricter rejection thresholds, and give little basis for any conclusions.}
  \label{tbl:fdp-sim}
  \end{table}

  These estimates corroborate \citet{Benjamin:2018gh}'s suggestion that reducing the statistical significance threshold may improve replicability, at least regarding the directional FDP of the original statistical hypotheses (of course, there is no way to account for potential change in researcher's behavior in response to the lowered threshold). Shall this be of interest, this method provides an empirical way to determine a better significance threshold, as no replications are needed. Nonetheless, potential effect heterogeneity is often a bigger concern. In this case, we are more concerned about the directional FDP for replications, which remains unacceptably high and requires replication experiments. Note, however, that a replication with low power could contribute to our estimates, even if there were no type S error.

\subsection{Effect shift}

  We performed the selective $z$-test for the hypothesis $H^E: \theta_O = \theta_R$ while adjusting for selection, where seven ($15\%$) studies are rejected. In contrast, without adjusting for selection, $18$ ($39\%$) studies are rejected at $0.05$ significance. If we wish to correct for multiplicity, we can apply Benjamini--Hochberg procedure \citeyearpar{Benjamini:1995cd}, which rules five ($11\%$) replication studies as inconsistent with the original studies at false discovery rate $0.10$.\footnote{The five rejected studies are \citet{Dodson:2008ks,vanDijk:2008br,PurdieVaughns:2008en,Farris:2008ev,Larsen:2008tu}.} Applying the more stringent Holm's method \citeyearpar{Holm:1979hl} to control the familywise error rate rules only the replication of \citet{Farris:2008ev} as inconsistent at familywise error rate $0.05$.

  We inverted the test for the hypothesis $H^E$, to yield a predictive interval for $Z_R$ and hence a predictive interval for the replication effect size estimate $\htheta_R$, shown in \Cref{fig:pi}. By definition $H^E$ is rejected when $\htheta_R$ is not included in the predictive interval. Adjusting for selection generally stretches the predictive intervals, resulting in fewer rejections.

  We also inverted the test for $H^{E,\delta}$ and obtained a confidence interval for the effect shifts, $\theta_O - \theta_R$, given in \Cref{fig:ci}. By construction the null hypothesis $H^E: \theta_O = \theta_R$ is rejected when the confidence interval does not include $0$. Adjusting for selection also generally lengthens the confidence intervals, resulting in fewer rejections.

  \begin{figure}[htbp]
    \centering
    \includegraphics[width=\hsize]{pi}
    \caption{Predictive intervals for $\htheta_R$, both adjusted and unadjusted for selection, overlay with a plot of $\htheta_R$ against $\htheta_O$. Studies 36 and 145 are not shown here. By definition we reject $H_0: \theta_O = \theta_R$ whenever the replication effect size estimate lies outside of the predictive interval. The intervals are generally longer after adjusting for selection.}
  \label{fig:pi}
  \end{figure}
  \begin{figure}[htbp]
    \centering
    \includegraphics[width=\hsize]{ci}
    \caption{Confidence intervals for $\theta_O - \theta_R$, both adjusted and unadjusted for selection. By construction the null hypothesis $H_0: \theta_O = \theta_R$ is rejected when the confidence interval does not include $0$. Many of the adjusted intervals are fairly long as either the replication studies suffer low power or the original effect size estimate is near the rejection threshold. The intervals are generally longer after adjusting for selection.}
  \label{fig:ci}
  \end{figure}

  If all procedures are replicated perfectly, we should expect to reject $5\%$ of the tests on average, rather than the observed $15\%$, and after the Benjamini--Hochberg correction, there would be no rejection with $90\%$ probability. In other words, while selection bias can partly explain the discrepancies between the original and replication studies, it does not explain all of it. Nevertheless, the RP:P data cannot be taken as strong evidence of widespread failure by replication teams to satisfactorily repeat the same experiment performed in the original study. The lack of strong evidence is hardly surprising: if the original study lacks power \citep{Morey:2017} or $\htheta_O$ is closed to the rejection boundary, little can be said about $\theta_O$ and hence $\theta_O - \theta_R$. Furthermore, the replication sample sizes were determined based on the original effect size to achieve at least $80\%$ in power. Selection bias inflated the original effect size, leading to lower test power and statistically insignificant replications \citep{Etz:2016gx,Camerer:2018de}. The lack of information about $\theta_O - \theta_R$ is evident in generally wider confidence intervals after adjustment in \Cref{fig:ci}.

\subsection{Effect decline}

  Finally, we considered the proportion of effect sizes that declined. Using the selective $z$-test, we tested the hypothesis $H^D$, conditioning on the event where the $z$-scores are observed and the variable $S$. The resulting $p$-values are given in \Cref{fig:effect-decline}. Our underestimate and overestimate are $35\%$ ($=16/46$) and $100\%$ respectively, with a $90\%$ confidence interval of $(11\%, 100\%)$.
  \begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{effect-decline}
    \caption{Histogram of the $p$-values for the null hypothesis $\theta_R \ge \theta_O$. $p$-values to the left gives more evidence for $\theta_R < \theta_O$ whereas $p$-values to the right gives more evidence for $\theta_R \ge \theta_O$. The estimate of the expected number of null $p$-values within each bin is given by the horizontal red line.}
  \label{fig:effect-decline}
  \end{figure}

  More generally, we used the hypothesis $H^{D,\rho}$ to estimate the proportion of effect sizes that declined by at least a fraction of $\rho$. The underestimate, overestimate and the $90\%$ confidence interval are given in \Cref{fig:effect-decline-range}. For example, we estimate that $16$ of the $46$ effect sizes ($35\%$ (with a $95\%$ lower confidence bound $11\%$) decreased by at least $20\%$, even after adjusting for selection on measurement noise. Note that this does not exclude explanations by other forms of selection, e.g.\ selecting a large effect when there is a random effect.
  \begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{effect-decline-range}
    \caption{The underestimate, overestimate and the $90\%$ confidence interval. The lower black line is the underestimate, the high black line is the overestimate and the gray band is the $90\%$ confidence interval.}
  \label{fig:effect-decline-range}
  \end{figure}

\section{Discussion}
\label{sec:discussion}

\subsection{Importance of adjusting for selection bias}

  As we have seen, selection bias plays a powerful and pervasive role in shaping the data we observe in large-scale replication studies (and, by extension, the data we observe in published studies that have not yet been replicated!). It leads to many predictable pathologies and should be viewed as a proverbial ``elephant in the room'' whenever we discuss descriptive statistics computed from such studies. In particular, we should avoid leaping to any conclusions about how many false claims there were in the original studies, whether effect sizes declined or by how much, or which replication studies suffered from infidelities, until we have carefully ruled out the possibility that publication bias alone is to blame for whatever descriptive statistic we have computed.

  Fortunately, the truncated Gaussian model, properly combined with modern multiple testing and post-selection inference methods, opens many avenues for analyses that directly answer questions about true effect sizes with appropriate uncertainty quantification. We have explored several such avenues here \citep[see also][]{Andrews:2018vh} but many others are possible.

\subsection{Importance of statistical formality}

  In addition, we hope this article serves to advocate for the benefits of careful formal statistical modeling in analyzing replication studies, in place of (or in addition to) descriptive statistics. In particular, using vaguely specified models or eschewing models altogether can lead to analyses from which it is difficult to draw firm conclusions. For example, in \citet{OpenScienceCollaboration:2015cn}, McNemar's test was applied to a $2 \times 2$ contingency table of whether the original and replication studies are equally likely to be statistically significant. The very small $p$-value reported for this test establishes nothing more than that the original studies were selected to be statistically significant, a fact which is likely already known by most in the field. In fact, the test does not quite establish even that, because it is unclear whether this hypothesis would be true even without the effect of selection bias: The proportion of statistically significant $p$-values is a measure of the average power, which depends on the sample sizes, and the sample sizes often differed substantially between the original and replication studies.

  Another example is RP:P's use of sample correlation coefficients between independent and dependent variables as a standardized measure of effect size for comparison between the original and replication studies. This comparison implicitly assumes that the distribution of the independent variable is the same in the original and replication studies, an assumption that was violated by many of the replications. In an extreme case, an ANOVA in \citet{PurdieVaughns:2008en} with race as one of the factors used $40$ African Americans and $37$ Whites, but was replicated with $120$ African Americans and $1370$ Whites. With such a dramatic change in the distribution of an independent variable, there is no reason why the correlation coefficients should remain the same, as illustrated in the following example.

  \begin{example}
  \label{eg:unbal-t}
    A study with a two-sample $t$-test for some treatment condition is replicated. Suppose the treatment and control group are drawn from $N(1, 1)$ and $N(0, 1)$, respectively. If the ratio of the two group sizes changes from one study to another, the correlation coefficients may differ as well, even without any infidelities or hidden moderators. Borrowing the numbers from \citet{PurdieVaughns:2008en} for instance, if the original study contains $40$ treatment and $37$ control units, the true correlation coefficient is $0.45$, whereas in a replication with $120$ control and $1370$ treatment units the true coefficient is $0.26$ instead.
  \end{example}

  Replication projects similar to RP:P have since materialized, but few stated an explicit statistical hypothesis. For example, in economics, \citet{Camerer:2016cx} used the same flawed metric of proportion of statistically significant results in the original direction. A statistical analysis with explicitly stated models and hypotheses will give us more meaningful estimates, particularly valuable given how costly these large scale replication efforts are.

\subsection{Interpretation of effect shifts}

  While we have proposed several methods for quantifying discrepancies between the effect sizes in the original and replication studies, the data alone cannot tell us why they might differ. Several potential explanations include:
  \begin{enumerate}
  \item design failures, systematic biases or calculation errors in either the original or the replication study;
  \item major differences in experimental conditions between the original and replication studies, which most researchers would recognize {\em a priori} as likely to affect the results; which \citet{Gilbert:2016he} call {\em infidelities}; and
  \item minor differences in experimental conditions between the studies --- such as lighting, weather, or the passage of time --- which cannot all be controlled but whose effects may nevertheless alter the true effect size in unforeseeable ways, often referred to as {\em hidden moderators} \citep[e.g.][]{Srivastava:2015}.
  \end{enumerate}

  While there may be no sharp distinction in principle between infidelities and hidden moderators, there is a scientifically crucial difference between moderating factors that can be anticipated by experimenters and those that cannot. If we can anticipate in advance when replications are likely to fail by carefully evaluating their designs, we might hope to solve the problem simply by being more careful in setting up experiments. By contrast, if hidden moderators confound most attempts to replicate most psychological studies, it would raise profound questions about the entire enterprise of experimental psychology. In the extreme case, if even trivial changes to those conditions have large and unpredictable effects on most phenomena of interest, we might begin to despair of gaining generalizable knowledge about psychology through laboratory experimentation.

  Our analyses point to several conclusions regarding effect shifts: First, that there are a few studies where we can be confident the effect in the replication study was significantly different than in the original study; second, that in aggregate, when effects do shift, they tend to decline (shift toward zero) in replications rather than increase; and third, that there is insufficient evidence to conclude that the vast majority of experimental effects simply evaporated upon replication. In particular, 83\% should not be treated as a reasonable estimator of the fraction of {\em true} effect sizes that declined; rather, it likely reflects that the estimates in the original studies overestimated their corresponding true effects due to selection bias.

  One possible explanation for systematically declining effect involves a subtler form of selection bias, where every experiment's effect size is random, buffeted by hidden moderators, and those experiments whose moderators primarily magnify the effect size are more likely to be published. That is, in the same way that experimenters select studies whose sampling error is large, they also selects for studies whose true effect size is larger than usual. Further systematic replication studies may help to shed light on which factors are most often the culprits in moderating true effect sizes, possibly improving the reliability of experiments and leading to new scientific insights \citep{Barrett:2015vl,Klein:2018}.

\subsection{Future work}

  As large-scale replicability studies are becoming more common in assessing the ``well-being'' of a scientific domain, this paper serves as a stepping stone for improving methodologies in future replicability studies.

  First, selection for significance is an inevitable consequence of the current scientific process. Our adjustments for selection is admittedly crude, but necessitated by the limitations in the given data. With more available information, a better model for selection can be used. For example, with the advancement of preregistration, we can use the external comparison method to produce less conservative estimates of the directional FDP at level $\alpha = 0.05$ if we have more information about statistically nonsignificant studies. With more replications carried out, we can estimate the publication bias model in \citet{Andrews:2018vh} more precisely; together with higher powered design in replications \citep[e.g.][]{Camerer:2018de}, we can enhance the precision of our estimators and power of our tests.

  Second, we emphasized the importance of statistical formality. Our proposed criteria are based on clearly defined parameters. While these criteria may not suit all needs in future replicability studies, additional formal hypotheses can also be analyzed under the post-selection inference framework similarly.

  With our proposed criteria and procedures, researchers can perform more informative inferences than the current practice, and provide a clearer picture of the replicability crisis.

\section*{Reproducibility}

  A git repository containing with the code generating the images in this article is available at \url{https://kenhung@bitbucket.org/kenhung/reproducibility-in-psychology.git}.

\section*{Acknowledgment}

  We thank Marcel A L M van Assen, Yoav Benjamini, Dean Eckles, Philip B Stark, Jacob Steinhardt, Jonathan Taylor, Alexa Tulett, Stefan Wager, Daniel Yekutieli, and Bin Yu for helpful comments and discussions.

\Urlmuskip=0mu plus 1mu\relax
\bibliographystyle{plainnat}
\bibliography{papers,additional}

\end{document}

### 2019-03-15 slides.tex
public branch made

% LAST UPDATED FOR 2019 SPRING GROUP MEETING

\documentclass{beamer}
\usecolortheme[RGB={109,121,147}]{structure}
\usetheme{Boadilla}
\setbeamercovered{invisible}

\setbeamertemplate{frametitle continuation}{}

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage[round]{natbib}
\usepackage{lmodern}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{xcolor}
\definecolor{color0}{HTML}{8A94A9}
\colorlet{l-color0}{color0!50}

\newcommand{\EE}{\mathbb{E}}
\newcommand{\FF}{\mathcal{F}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\cH}{\mathcal{H}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\se}{se}
\DeclareMathOperator{\sgn}{sign}

\newcommand{\hdelta}{\hat{\delta}}
\newcommand{\hmu}{\hat{\mu}}
\newcommand{\hsigma}{\hat{\sigma}}
\newcommand{\htheta}{\hat{\theta}}
\newcommand{\ao}{\alpha_0}
\newcommand{\gest}{\ge_\text{st}}
\newcommand{\vs}{\vskip+1em}

\graphicspath{{./fig/}}

\AtBeginSection[]{
  \begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}
}

\title[Replicability Assessment]{Statistical Methods for Replicability Assessment}

\author[Hung \& Fithian]{Kenneth Hung and Will Fithian}
\institute[UC Berkeley]{
	University of California, Berkeley \\
	\medskip
	\textit{\{kenhung, wfithian\}@berkeley.edu}
}
\date{March 12, 2019}

\begin{document}

\begin{frame}
	\titlepage
\end{frame}

\iffalse
\begin{frame}
  \frametitle{First Author}
  \begin{center}
    \includegraphics[width=.5\textwidth]{kenneth-github.jpeg}\\
    Kenneth Hung (UC Berkeley Math)
  \end{center}
\end{frame}
\fi

\section{Reproducibility Project: Psychology}

\begin{frame}{Introduction: Replicability Crisis}
   \centering
   \includegraphics[width=0.8\textwidth]{nyt-title.png}
   \vs
   \includegraphics[width=0.8\textwidth]{nyt-body.png}
\end{frame}

\begin{frame}{Introduction: Replicability crisis}
  Social psychology facing urgent crisis in replicability of results
  % Oral: "Facing" as active verb: other fields have problems but they aren't facing it the way psych is
  \vs
  Commonly attributed to varied factors
  \begin{itemize}
	  \item selection for significance
	  \item $p$-hacking, questionable research practices (QRPs)
	  \item fraud
	  \item infidelity of replication experimental designs
	  \item flaws in original experimental designs
	  \item ``Hidden moderators'': subtle, uncontrollable differences in experimental conditions
  \end{itemize}
  % Oral: It makes quite a difference which of these is to blame, as I'll explain
  \vs
  Reproducibility Project:\ Psychology
  \begin{itemize}
	  \item Preregistered replications of $100$ studies published in 2008 in three top psych.\ journals
	  \item Massive collaborative effort by hundreds of researchers
  \end{itemize}
\end{frame}

\begin{frame}{Results from RP:P}
  RP:P reported descriptive statistics:
  \begin{itemize}
	  \item $36\%$ of replications significant in same direction as original study
	  \item $47\%$ of original point estimates in replication studies' $95\%$ CIs
	  \item $83\%$ of the effect size estimates declined ($\htheta_{i,R}/\htheta_{i,O} < 1$)
  \end{itemize}
  \vs 
  Widely reported as damning result:
  \begin{itemize}
	  \item {\em Washington Post}: ``... affirms that the skepticism [of published results] was warranted'' \citep{Achenbach:2015vi}
	  \item {\em Economist}: ``... managed to replicate satisfactorily the results
	    of only $39\%$ of the studies investigated'' \citep{Anonymous:uoQKTVTm}
	  \item {\em New York Times}: ``more than half of the findings did not hold up when retested'' \citep{Carey:2015wp}
  \end{itemize}
\end{frame}

\begin{frame}{Debate}
  What should we make of these numbers?
  \begin{itemize}
  	\item e.g.\ $47\%$ of original point estimates in replication studies' $95\%$ CIs 
  \end{itemize}
  \vs
  \citet{Gilbert:2016he} critiqued $47\%$ number:
  \begin{itemize}
	  \item Confidence interval $\ne$ predictive interval
	  \item No replication is exact ($\theta_{i,O} \ne \theta_{i,R}$)
	  \item Low fidelity of some replications (e.g.\ race questionnaire in Italy)
	  \item ``OSC seriously underestimated the reproducibility of psychological science''
  % Oral: not really fair in the sense that OSC didn't really estimate anything!
  \end{itemize}
  \vs
  Further debate between defenders \citep{Anderson:2016gs,Srivastava:2016,Nosek:2016}, critics \citep{Gilbert:2016uv,Gilbert:2016th}
\end{frame}

\begin{frame}{What estimand?}
  Did OSC ``underestimate replicability?''
  \vs
  First need to answer: what is the estimand?
  \vs
  RP:P offers
  \begin{itemize}
  	\item descriptive statistics
  	\item tiny $p$-values for tests of very strong nulls 
    \begin{itemize}
    	\item e.g.\ McNemar's test of whether orig.\ studies more likely to be significant at level $0.05$
    \end{itemize}
  	\item no attempt to define target of inference
  	\item no attempt to disentangle sources of error
  \end{itemize}
\end{frame}

\begin{frame}{Selection for significance}
  \centering
  RP:P data: unmistakable sign of selection at $\alpha = 0.05$

  \includegraphics[width=0.8\textwidth]{ecdf.pdf}

  {\color{red} Can this alone explain all results?}
\end{frame}

\begin{frame}{Simulation: Selection bias}
  Can selection bias alone explain RP:P's descriptive statistics?
  \vs
  Simulation experiment
  \begin{itemize}
  \item all original / replication studies: same effect size $\theta$
  \item Gaussian estimators $\htheta_{i,O}, \htheta_{i,R}$, $\text{s.e.} = 1$
  \item observe pair only when $|\htheta_{i,O}| > z_{\alpha/2}$
  \end{itemize}
  \vs
  Plot descriptive statistics as function of $\theta$
\end{frame}

\begin{frame}{Simulation: Selection bias}
  \centering
  {\bf Question:} with $\theta = 1/2$, what fraction of repl.\ CIs cover orig.\ estimates?
  \vs
  \pause
  \includegraphics[width=0.5\textwidth]{naive-ci-theta05.pdf}
  \vs
  {\bf Answer:} $\approx 50\%$
\end{frame}

\begin{frame}{Simulation: Selection bias}
  \centering
  \includegraphics[width=0.8\textwidth]{naive-ci-sim.pdf}
\end{frame}

\begin{frame}{Simulation: Selection bias}
  \centering
  \includegraphics[width=0.8\textwidth]{naive-same-dir.pdf}
\end{frame}

\begin{frame}{Simulation: Selection bias}
  \centering
  \includegraphics[width=0.8\textwidth]{naive-decline.pdf}
\end{frame}

\begin{frame}{Selection bias}

  Selection bias is basic feature of data
  \begin{itemize}
  \item Qualitatively, can explain RP:P metrics
  \item Can't learn anything else from data unless we adjust for it
  \end{itemize}
  \vs
  Different explanations suggest different priorities for reform, e.g.:
  \begin{itemize}
  \item Selection bias: publish negative results, post-hoc stat.\ adjustment
  \item Infidelities: more detailed methods sections?
  \item Hidden moderators: abandon experimental psychology?
  \end{itemize}
  \vs
  Key tools:
  \begin{itemize}
  \item conditional post-selection inference \citep[][many others]{Lee:2016fv, Fithian:2014ws}
  \item ideas from multiple testing \citep[][many others]{Benjamini:1995cd,Storey:2002vj,Heller:2007}
  \end{itemize}
\end{frame}

\section{Formalizing replicability}

\begin{frame}{A model for replications}
  Model for original (O) / replication (R) study pair $i = 1, \ldots, m$:
  \begin{equation}
  	\htheta_{i,O} \sim N\left(\theta_{i,O}, \;\sigma_{i,O}^2\right) 1_{\{|\htheta_{i,O}| > c\}} \quad\text{ and }\quad \htheta_{i,R} \sim N\left(\theta_{i,R}, \;\sigma_{i,R}^2\right)
  \label{eq:model}
  \end{equation}
  Can formalize three definitions in terms of parameters of model \eqref{eq:model}
  \begin{itemize}
  	\item Some hypotheses defined in terms of $S_i = \sgn(\htheta_{i,O})$
  \end{itemize}
  \vs
  Finite population model:
  \begin{itemize}
  	\item no assumptions on dist.\ of $(\theta_{i,O}, \theta_{i,R})$ 
  	\item agnostic to why $\theta_{i,O} \ne \theta_{i,R}$ 
  \end{itemize}
\end{frame}

\begin{frame}{Defining replicability}
  What do we estimate when we ``estimate replicability?''
  \vs
  {\bf RP:P statistic 1:} $36\%$ of replications significant in same direction as original study
  \vs
  {\bf Definition 1:} False directional claims
  \begin{itemize}
	  \item {\em What fraction of original directional claims were wrong?}
	  \item Psychology as enterprise in large-scale multiple testing
	  \item {\em Type S error:} true effect 0 or opposite sign as claimed \citep{Gelman:2000tg}
	  \item Would it be different if we used a lower publication threshold?
  \end{itemize}
  \vs
  Answers question: ``Would an exact replication with huge $n$ affirm the directional claim?''
\end{frame}

\begin{frame}{Formalizing replicability}

  {\bf Definition 1:} False directional claims
  \vs
  \begin{center}
  	{\em What fraction of original directional claims were wrong?}
  \end{center}
  \vs
  Null hypothesis for Type S error:
  \[
  	H_i^{S,O}:\;\; {\color{red} S_i} \cdot \theta_{i,O} \le 0
  \]
  \vs
  Directional FDP for all experiments with $p_{i,O} < \alpha$:
  \[
  	\text{FDP}_{\alpha} = \frac{\#\{i: H_i^{S,O} \text{ true}, \;p_{i,O} < \alpha\}}{\#\{i: p_{i,O} < \alpha\}}
  \]
  \vs
  Does it improve if $\alpha = 0.005$ were used instead? \citep{Benjamin:2018gh}
\end{frame}

\begin{frame}{Defining replicability}
  What do we estimate when we ``estimate replicability?''
  \vs
  {\bf RP:P statistic 2:} $47\%$ of orig.\ point estimates in repl.\ studies' $95\%$ CIs
  \vs
  {\bf Definition 2:} Effect shift of replication
  \begin{itemize}
	  \item {\em How much do effect sizes shift from original to replication?}
	  \item Stability across direct replications
	  \item Bare minimum form of external validity
	  \item Identify studies where effect definitely shifted, produce CIs for shifts
  \end{itemize}
  \vs
  Answers question: ``Can psychologists successfully replicate experimental conditions?'' 
\end{frame}

\begin{frame}{Formalizing replicability}

  {\bf Definition 2:} Effect shift of replication
  \begin{center}
    {\em How much do effect sizes shift from original to replication?}
  \end{center}
  \vs
  Construct CIs for $\theta_{i,O} - \theta_{i,R}$
  \vs
  Linear in natural parameters for truncated bivariate Gaussian family
  \vs
  Invert selective $z$-test \citep{Lee:2016fv} of 
  \[
  H_i^{E,\delta}:\; \theta_{i,O} - \theta_{i,R} = \delta
  \]
  \vs
  Which / how many CIs exclude $0$ (after multiplicity adjustment)?
\end{frame}

\begin{frame}{Selective $z$-test}
  \centering
  \begin{tikzpicture}
  \fill[l-color0] (-4, -3) -- (-4, 3) -- (-1, 3) -- (-1, -3) -- cycle;
  \fill[l-color0] (4, -3) -- (4, 3) -- (1, 3) -- (1, -3) -- cycle;
  \draw[thick, ->] (0, -3.25) -- (0, 3.25) node[above] {$z_2$};
  \draw[thick, ->] (-4.25, 0) -- (4.25, 0) node[right] {$z_1$};
  \draw[dashed] (-1, -3) -- (-1, 3);
  \draw[dashed] (1, -3) -- (1, 3);
  \fill (2, 0.5) circle(2pt) node[above right] {$(Z_1, Z_2)$};
  \draw[thick, ->] (0, 0) -- (2, -1) node[below right] {$\eta$};

  \draw[thick, <->] (0, 0) -- (0.6, 1.2) node[midway, left] {$M / \|\eta_\perp\|$};
  \draw[thick] (-3, 3) -- (-1, 2);
  \draw[thick, dashed] (-1, 2) -- (1, 1);
  \draw[thick] (1, 1) -- (4, -0.5) node[right] {$\ell$};

  \draw[thick, <->] (0.7, 1.4) -- (2.1, 0.7) node[midway, above] {$D / \|\eta\|$};
  \end{tikzpicture}
\end{frame}

\begin{frame}{Defining replicability}
  What do we estimate when we ``estimate replicability?''
  \vs
  {\bf RP:P statistic 3:} $83\%$ of the effect size estimates declined from original to replication
  \vs
  {\bf Definition 3:} Overall effect decline
  \begin{itemize}
  \item {\em What fraction of effect sizes declined by at least $20\%$?}
  \item Refers to {\em true} effect sizes, not point estimates
  \end{itemize}
  \vs
  Answers question: ``Do effects systematically attenuate in replications?'' 
\end{frame}

\begin{frame}{Defining replicability}

  {\bf Definition 3:} Overall effect decline
  \begin{center}
  	{\em What fraction of effect sizes declined by at least $20\%$?}
  \end{center}
  \vs
  Did replication $i$ show decline by at least $\rho \in [0,1]$?
  \[
  	H_i^{D,\rho}: S_i \cdot \theta_{i,R} \;\ge\; S_i \cdot (1-\rho) \theta_{i,O}
  \]
  % Oral: e.g. if rho = 20% and the original effect size was positive, the null hypothesis is theta_iR less than 0.8 times theta_iO$
  \vs
  After conditioning on $S_i$, this is a linear hypothesis in $(\theta_{i,R},\theta_{i,O})$
  \begin{itemize}
  	\item Use \citet{Lee:2016fv} test for individual $H_i^{D,\rho}$
  	\item Aggregate to estimate / bound fraction that declined by $\rho$
  \end{itemize}
\end{frame}

\section{Assessing replicability}

\begin{frame}{False directional claims}
  Work with adjusted $p$-values: conditionally, $p_{i,O} / 0.05 \gest U[0,1]$, under $H_i^{S,O}$
  \vs
  \begin{center}
  	\includegraphics[width=0.45\hsize]{fdp-original.pdf}
	\end{center}
  \vs
  {\bf NB:} no spike near 1 ($p_{i,O} \approx 0.05$)
\end{frame}

\begin{frame}{Inference on $\text{FDP}_{0.05}$}
  \begin{center}
  \begin{tabular}{lccc}
    \hline
    Adjusted $p$-value & $H_i^{S,O}$ true & $H_i^{S,O}$ false & Total \\
    \hline
    $20p_{i,O} \le \lambda$ & $*$ & $*$ & $*$ \\
    $20p_{i,O} > \lambda$ & $U$ & $*$ & $B$ \\
    Total & $V_{0.05}$ & $*$ & $R_{0.05} = m$ \\
    \hline
  \end{tabular}
  \end{center}
  \vs
  Inferences based on:
  \begin{equation}\label{eq:B}
    B \ge U \gest \text{Binom}(V, 1-\lambda)
  \end{equation}
  $\EE B \geq (1-\lambda)V_{0.05}$ leads to estimator \citep{Storey:2002vj}:
  \[
  	\widehat{\text{FDP}}_{0.05} = \frac{B}{R_{0.05}(1-\lambda)} = 2B/m \;\; \text{ if } \lambda = 1/2
  \]
  \vs
  \eqref{eq:B} also gives UCB $V_{0.05}^*$, leads to UCB 
  \[
  	\text{FDP}_{0.05}^{*} =  V_{0.05}^* / R_{0.05}
  \]
\end{frame}

\begin{frame}{Related questions}
  So far, asking about Type S error:
  \begin{itemize}
  	\item Does $S_i$ is correctly describe $\sgn(\theta_{i,O})$? (true orig.\ effect)
  \end{itemize}
  \vs
  Two related questions:
  \begin{itemize}
  	\item Does $S_i$ correctly predict $\sgn(\theta_{i,R})$? (true repl.\ effect)
  	\item Would Type S error be better if we'd used a different threshold, e.g.\ $0.005$?
  \end{itemize}
  \vs
  Requires slightly more subtle methods, similar in spirit  
\end{frame}

\begin{frame}{Results: False directional claims}
	Note:
	\begin{itemize}
		\item Estimate FDP $\approx 32\%$ for $0.05$ threshold
		\item For $\alpha = 0.005$, estimate is $7\%$, UCB $18\%$
		\item But not clear that FDP for replications is improved
		\item Numbers {\color{red} overestimate} Type S error ($\theta = 0.001$ similar to $0$).
	\end{itemize}
	\vs
	\centering
	Estimates / CIs for false directional claims
	\begin{tabular}{rr@{}lr@{}lrr}
	  \hline
	  $\alpha$ & Orig.\ Est. && Orig.\ U.C.B. && Repl.\ Est. & Repl.\ U.C.B. \\
	  \hline
	  $0.001$ & $2\%$& & $9\%$& & $27\%$ & $55\%$ \\
	  $0.005$ & $7\%$& & $18\%$& & $36\%$ & $61\%$ \\
	  $0.01$ & $11\%$& & $22\%$& & $39\%$ & $61\%$ \\
	  $0.05$ & $32\%$ && $47\%$ && $47\%$ & $63\%$ \\
	  \hline
	\end{tabular}
\end{frame}

\begin{frame}{Results: Effect shift}
  We construct $95\%$ CIs for $\theta_{i,O}-\theta_{i,R}$:
  \begin{itemize}
	  \item $15\%$ of studies exclude $0$ (exact replication), adjusting for selection
	  \item $39\%$ of studies rejected, otherwise
	  \item $11\%$ exclude $0$ after $\text{BH}_{0.1}$ correction, $1$ after Bonferroni
  \end{itemize}
\end{frame}

\begin{frame}{Results: Effect shift}
	\centering
	\includegraphics[width=0.75\hsize]{ci.pdf}
\end{frame}

\begin{frame}{Results: Effect decline}
  Estimate $35\%$ of effects declined by at least $20\%$
	\centering
	\includegraphics[width=0.8\hsize]{effect-decline-range.pdf}
\end{frame}

\begin{frame}{Takeaways}
  Selection bias is a powerful force
  \begin{itemize}
	  \item Leads to many predictable pathologies
	  \item Can't learn anything else without accounting for it
	  \item Truncated Gaussian model opens many avenues for inference
  \end{itemize}
  \vs
  Replicability has many possible meanings
  \begin{itemize}
  	\item Precisely specifying estimand is essential for meaningful discussions
  \end{itemize}
  \vs
  Rate of Type S errors in experimental psych is high: ($\approx 32\%$ of publ.?)
  \begin{itemize}
  	\item Reducing threshold to $0.005$ seems to improve FDP w.r.t.\ orig.\ effects
  	\item Doesn't mean results will be replicable in new experiments
  \end{itemize}
  \vs
  Evidence in a few studies that true effect sizes differ substantially
  \vs
  Some evidence of systematic effect decline (need more data)
\end{frame}

\begin{frame}{Future work}
\begin{itemize}
	\item Preregistration
	\begin{itemize}
		\item Better publication bias model
		\item Less conservative estimate: information of nonsignificant studies are useful still!
	\end{itemize}
	\item Higher powered design, e.g.\ \citet{Camerer:2018de,Klein:2018}
  \item More formal criteria
  \item Clearer picture of the replicability crisis
\end{itemize}
\end{frame}

\begin{frame}
\centering
{\Large Thanks!}
\end{frame}

\begin{frame}[allowframebreaks]{References}
\footnotesize{
\bibliography{papers,additional}
\bibliographystyle{plainnat}
}
\end{frame}

\end{document}

### 2019-03-15 supplement.tex
public branch made

\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{enumitem}
\newlist{inlinelist}{enumerate*}{1}
\setlist*[inlinelist]{label=(\arabic*)}
\usepackage[totalwidth=450pt, totalheight=630pt]{geometry}
\usepackage{graphicx}
\PassOptionsToPackage{hyphens}{url} % pass options to url autoloaded by hyperref
\usepackage[pdfencoding=auto, psdextra]{hyperref} % hyperref must be loaded before cleveref
\usepackage{mathrsfs}
\usepackage{multirow}
\usepackage[round]{natbib} % natbib must be loaded before algorithm2e
\usepackage[linesnumbered, ruled]{algorithm2e} % algorithm2e must be loaded before cleveref
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{verbatim}
\usepackage{xcolor}

\interfootnotelinepenalty=10000

\captionsetup{width=0.8\textwidth}

\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{lemma}[corollary]{Lemma}
\newtheorem{proposition}[corollary]{Proposition}
\newtheorem{theorem}[corollary]{Theorem}

\theoremstyle{definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}
\newtheorem*{remark}{Remark}

\newtheoremstyle{custom}{}{}{\itshape}{}{\bfseries}{.}{.5em}{\thmnote{#3}}
\theoremstyle{custom}
\newtheorem*{customthm}{Theorem}

\setlength{\tabcolsep}{1em}
\setlist{listparindent=\parindent, parsep=0pt}

\newcommand{\EE}{\mathbb{E}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\cH}{\mathcal{H}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\se}{se}
\DeclareMathOperator{\sgn}{sign}

\newcommand{\hdelta}{\hat{\delta}}
\newcommand{\hmu}{\hat{\mu}}
\newcommand{\hsigma}{\hat{\sigma}}
\newcommand{\htheta}{\hat{\theta}}
\newcommand{\ao}{\alpha_0}
\newcommand{\gest}{\ge_\text{st}}

\newcommand{\WFcomment}[1]{{\color{red!40!gray} (WF: #1)}}
\newcommand{\KHcomment}[1]{{\color{green!40!gray} (KH: #1)}}

% Uncomment this line to get rid of my comments
% \renewcommand{\WFcomment}[1]{}
% \renewcommand{\KHcomment}[1]{}

\graphicspath{{./fig/}}

\begin{document}

\title{Supplement to ``Statistical Methods for Replicability Assessment''}
\date{\today}
\author{
  Kenneth Hung\thanks{Department of Mathematics, University of California, Berkeley} \and
  William Fithian\thanks{Department of Statistics, University of California, Berkeley}
}
\maketitle

\section{\texorpdfstring{$t$}{t}-tests and ANOVAs}

  Both $t$-tests and $F(1, \cdot)$ ANOVAs, whether they are within-subject or between-subject, one-way or multi-way, can be thought of as testing some contrast $\delta$ of the true cell means.

  We can construct unbiased estimators $\hdelta$ and $\hsigma^2$ for the contrast and the common variance from the homoscedasticity assumption. The standard error can be written as $\frac{\sigma}{k}$ where $\sigma^2$ is the true variance and $k$ is some known constant determined by the cell sizes. We can now test the null hypothesis $\delta = 0$ using the $t$-statistic $T = k \hdelta / \hsigma$. If there is an effect, i.e.\ $\delta \ne 0$, then $T$ follows the noncentral $t$-distribution
  \[
    T \sim t_{df}\left(k\frac{\delta}{\sigma}\right).
  \]
  We take the effect size $\theta$ to be $\delta / \sigma$.

  For notation, we will use subscripts to indicate the cell. We will use $\mu_i$ (or, $\mu_{ij}$ or $\mu_{ijk}$) to denote the population mean in each cell. For the marginals, we use $*$ to indicated dimensions averaged out. For example, in a $2 \times 3$ ANOVA,
  \[
    \mu_{1*} = \frac{\mu_{11} + \mu_{12} + \mu_{13}}{3}.
  \]
  For designs with between-subject factor(s), the subject can be naturally grouped, we will use $I_i$ (or $I_{ij}$) to indicate these groups. The number of subjects in each is $n_i$ (or $n_{ij}$) respectively. For example, if there are two between-subject factors, each with two levels, we have four groups $I_{11}$, $I_{12}$, $I_{21}$ and $I_{22}$, and their sizes are $n_{11}$, $n_{12}$, $n_{21}$ and $n_{22}$ respectively.
  Finally, when a subject is specified and their between-subject factor is clear from the context, we may omit the index as $\cdot$.

  \paragraph{Study 1: \citet{Roelofs:2008ik}}
  The study has a $2 \times 2 \times 2$ within-subject design and we are interested in the two-way interaction between the second and third factors. In other words, we want to test if
  \[
  \delta = \mu_{*11} - \mu_{*12} - \mu_{*21} + \mu_{*22}
  \]
  is zero.

  We can test it by finding an unbiased estimator of this, and divide it by its standard error estimate to give a $t$-statistic. A natural estimate is
  \[
  \hdelta = \frac{1}{n} \sum \lambda' X^{(i)},
  \]
  where $\lambda' = (\frac{1}{2}, -\frac{1}{2} ,-\frac{1}{2}, \frac{1}{2}, \frac{1}{2}, -\frac{1}{2}, -\frac{1}{2}, \frac{1}{2})$ and $X_{(i)}$ is the observation 
  \[
  (X_{111}, X_{112}, X_{121}, X_{122}, X_{211}, X_{212}, X_{221}, X_{222})'
  \]
  for individual $i$. We can view $\lambda' X^{(i)}$ as the observations and perform a one-sample $t$-test. We have reanalyzed the replication data and confirmed that our test is equivalent.

  Hence the test statistic $T$ follows $T \sim t_{n-1}(\sqrt{n} \theta)$, where $\theta = \delta / \sigma$ and $\sigma^2$ is the variance of $\lambda' X^{(i)}$. We have $n_O = 14$ and $n_R = 29$.

  \paragraph{Study 2: \citet{Morris:2008dm}}
  The study is a within-subject one-way ANOVA. In other words, we want to test if
  \[
  \delta = \mu_1 - \mu_2
  \]
  is zero. A natural estimate for $\delta$ is
  \[
  \hdelta = \frac{1}{n} \sum \lambda' X^{(i)},
  \]
  where $\lambda' = (1, -1)$ and $X^{(i)}$ is the observation $(X_1, X_2)'$ for individual $i$. We can now view $\lambda' X^{(i)}$ as the observations and perform a one-sample $t$-test. We have reanalyzed the replication data and confirmed that our test is equivalent.

  Hence the test statistic $T$ follows $T \sim t_{n-1}(\sqrt{n} \theta)$, where $\theta = \lambda' (\mu_1, \mu_2) / \sigma$ and $\sigma^2$ is the variance of the contrast. We have $n_O = n_R = 24$.

  \paragraph{Study 3: \citet{Liefooghe:2008bd}}
  The RP:P dataset describes this as a multivariate ANOVA, but upon inspection of its code (\url{https://osf.io/69b27/}) we recognize the test of interest is in fact a paired $t$-test of two components of the multivariate observation. We can consider the differences as the observations. Hence the test statistic $T$ follows $T \sim t_{n-1}(\sqrt{n} \theta)$, where $\theta = (\mu_1 - \mu_2) / \sigma$ and $\sigma^2$ is the variance of the difference. We have $n_O = 25$ and $n_R = 32$.

  \paragraph{Study 4: \citet{Storm:2008bt}}
  The study is a $2 \times 2$ mixed design with the first factor being within-subject and the second factor being between-subject. We are interested in the interaction. In other words, we want to test if
  \[
  \delta = \mu_{11} - \mu_{12} - \mu_{21} + \mu_{22}
  \]
  is zero. A natural estimate for $\delta$ is
  \[
  \hdelta = \frac{1}{n_1} \sum_{i \in I_1} \lambda' X^{(i)} - \frac{1}{n_2} \sum_{i \in I_2} \lambda' X^{(i)},
  \]
  where $\lambda' = (1, -1)$ and $X^{(i)}$ is the observation $(X_{1 \cdot}, X_{2 \cdot})'$ for subject $i$. We can view $\lambda' X_{(i)}$ as the observations and perform a two-sample $t$-test. We however cannot reanalyze the replication data to confirm that our test is equivalent as the data has since been removed (\url{https://osf.io/rj4u6/}).

  Hence the test statistic $T$ follows $T \sim t_{n_1 + n_2 - 2}\left(\left(\frac{1}{n_1} + \frac{1}{n_2}\right)^{-1/2} \theta\right)$, where
  \[
  \theta = \left(\lambda'(\mu_{11}, \mu_{21}) - \lambda'(\mu_{12}, \mu_{22})\right) / \sigma
  \]
  and $\sigma^2$ is the variance of $\lambda' X_{(i)}$. We have $n_{1O} + n_{2O} = 240$, $n_{1R} = 136$ and $n_{2R} = 134$ but $n_{1O}$ and $n_{2O}$ are unavailable.

  \paragraph{Study 5: \citet{Mitchell:2008hu}}
  The study has a $2 \times 2$ within-subject design and we are interested in the main effect of the first factor. In other words, we want to test if
  \[
  \delta = \mu_{1*} - \mu_{2*}.
  \]
  is zero. A natural estimate for $\delta$ is
  \[
  \hdelta = \frac{1}{n} \sum \lambda' X^{(i)},
  \]
  where $\lambda' = (\frac{1}{2}, \frac{1}{2}, -\frac{1}{2}, -\frac{1}{2})$ and $X^{(i)}$ is the observation $(X_{11}, X_{12}, X_{21}, X_{22})'$. We can view $\lambda' X^{(i)}$ as the observations and perform a one-sample $t$-test. We have reanalyzed the replication data and confirmed that our test is equivalent.

  Hence the test statistic $T$ follows $T \sim t_{n-1}(\sqrt{n} \theta)$, where $\theta = \delta / \sigma$ and $\sigma^2$ is the variance of $\lambda' X^{(i)}$. We have $n_O = 32$ and $n_R = 48$.

  \paragraph{Study 6: \citet{Berry:2008jh}}
  The test of interest is a paired $t$-test, same as Study 3. We define $\theta$ similarly, and have $n_O = 24$ and $n_R = 32$.

  \paragraph{Study 7: \citet{Beaman:2008df}} The test of interest is a paired $t$-test, same as Study 3. We define $\theta$ similarly, and have $n_O = 100$ and $n_R = 15$.

  \paragraph{Study 8: \citet{Dodson:2008ks}}
  The study has a $2 \times 2 \times 2$ mixed design with the first two factors being within-subject and the third factor being between-subject. We are interested in the three-way interaction. In other words, we want to test if
  \[
  \delta = \mu_{111} - \mu_{112} - \mu_{121} - \mu_{211} + \mu_{122} + \mu_{212} + \mu_{221} - \mu_{222}
  \]
  is zero. A natural estimate of $\delta$ is
  \[
  \hdelta = \frac{1}{n_1} \sum_{i \in I_1} \lambda' X^{(i)} - \frac{1}{n_2} \sum_{i \in I_2} \lambda' X^{(i)}
  \]
  where $\lambda' = (1, -1, -1, 1)$ and $X^{(i)}$ is the observation $(X_{11 \cdot}, X_{12 \cdot}, X_{21 \cdot}, X_{22 \cdot})'$ for subject $i$ and $\cdot$ is the appropriate index. We can view $\lambda' X^{(i)}$ as the observations and perform a two-sample $t$-test. We have reanalyzed the replication data and confirmed that our test is equivalent.

  Hence the test statistic $T$ follows $T \sim t_{n_1 + n_2 - 2}\left(\left(\frac{1}{n_1} + \frac{1}{n_2}\right)^{-1/2} \theta\right)$, where $\theta = \delta / \sigma$ and $\sigma^2$ is the variance of $\lambda' X^{(i)}$. We have $n_{1O} = 20$, $n_{2O} = 19$, $n_{1R} = 13$ and $n_{2R} = 20$.

  \paragraph{Study 10: \citet{GanorStern:2008hz}}
  The study has a $2 \times 3 \times 2$ mixed design with the first two factors being within-subject and the third factor being between-subject. We are interested in the main effect of the first factor. In other words, we want to test if
  \[
  \delta = \mu_{1**} - \mu_{2**}
  \]
  is zero. A natural estimate of $\delta$ is
  \[
  \hdelta = \frac{1}{n_1} \sum_{i \in I_1} \lambda' X^{(i)} + \frac{1}{n_2} \sum_{i \in I_2} \lambda' X^{(i)}
  \]
  where $\lambda' = (\frac{1}{6}, \frac{1}{6}, \frac{1}{6}, -\frac{1}{6}, -\frac{1}{6}, -\frac{1}{6})$ and $X^{(i)}$ is the observation $(X_{11 \cdot}, X_{12 \cdot}, X_{13 \cdot}, X_{21 \cdot}, X_{22 \cdot}, X_{23 \cdot})'$ for subject $i$. We can view $\lambda' X_{(i)}$ as the observations and assume that it has the same variance $\sigma^2$ across the groups. The variance of $\hdelta$ is thus $(\frac{1}{n_1} + \frac{1}{n_2}) \sigma^2$, and $\sigma^2$ can be estimated with the pooled variance. Hence we can test if $\delta = 0$ with a $t$-test with the null distribution
  \[
  T = \frac{\hdelta}{\sqrt{\frac{1}{n_1} + \frac{1}{n_2}} \hsigma} \sim t_{n_1 + n_2 - 2}\left(\left(\frac{1}{n_{11}} + \frac{1}{n_{22}}\right)^{-1/2} \theta\right)
  \]
  where $\theta = \delta / \sigma$. We have reanalyzed the replication data and confirmed that our test is equivalent. We have $n_{1O} + n_{2O} = 32$, $n_{1R} = 16$ and $n_{2R} = 15$ but $n_{1O}$ and $n_{2O}$ are unavailable.

  \paragraph{Study 11: \citet{Mirman:2008bz}}
  The study has a $2 \times 2$ within-subject design and we are interested in the main effect of the first factor. This is the same setup as Study 5, and hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have reanalyzed the replication data and confirmed that our test is equivalent. We have $n_O = 22$ and $n_R = 30$.

  \paragraph{Study 15: \citet{Schmidt:2008cd}}
  The test of interest is a paired $t$-test, same as Study 3. We defined $\theta$ similarly, and have $n_O = 95$ and $n_R = 242$.

  \paragraph{Study 19: \citet{Oberauer:2008kx}}
  The study has a $3 \times 2$ mixed design with the first factor being within-subject and the second factor being between-subject. We are interested in the main effect of the second fator. In other words, we want to test if
  \[
  \delta = \mu_{*1} - \mu_{*2}
  \]
  is zero. A natural estimate of $\delta$ is
  \[
  \hdelta = \frac{1}{n_1} \sum_{i \in I_1} \lambda' X^{(i)} - \frac{1}{n_2} \sum_{i \in I_2} \lambda' X^{(i)}
  \]
  where $\lambda' = (\frac{1}{3}, \frac{1}{3}, \frac{1}{3})$ and $X^{(i)} = (X_{1 \cdot}, X_{2 \cdot}, X_{3 \cdot})'$ for subject $i$. We can view $\lambda' X^{(i)}$ as the observations and perform a two-sample $t$-test. We have reanalyzed the replication data and confirmed that our test is equivalent.

  Hence the test statistic $T$ follows $T \sim t_{n_1 + n_2 - 2}\left(\left(\frac{1}{n_1} + \frac{1}{n_2}\right)^{-1/2} \theta\right)$, where $\theta = \delta / \sigma$ and $\sigma^2$ is the variance of $\lambda' X^{(i)}$. We have $n_{1O} = n_{2O} = 16$, $n_{1R} = 11$ and $n_{2R} = 10$.

  \paragraph{Study 20: \citet{Sahakyan:2008bi}}
  The study has a $2 \times 2$ mixed design with the first factor being between-subject and second factor being within-subject. We are interested in the interaction. This is the same setup as Study 4 and thus we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have reanalyzed the replication data and confirmed that our test is equivalent. We have $n_{1O} + n_{2O} = 96$, $n_{1R} = 47$ and $n_{2R} = 61$ but $n_{1O}$ and $n_{2O}$ are unavailable.

  \paragraph{Study 24: \citet{Bassok:2008kt}}
  The study has a $2 \times 2$ within-subject design. We are interested in the interaction. In other words, we want to test if
  \[
  \delta = \mu_{11} - \mu_{12} - \mu_{21} + \mu_{22}
  \]
  is zero. A natural estimate of $\delta$ is
  \[
  \hdelta = \frac{1}{n} \sum \lambda' X^{(i)}
  \]
  where $\lambda' = (1, -1, -1, 1)$ and $X^{(i)}$ is the observation $(X_{11}, X_{12}, X_{21}, X_{22})'$ for subject $i$. We can view $\lambda' X^{(i)}$ as the observations and perform a one-sample $t$-test. We have reanalyzed the replication data and confirmed that our test is equivalent.

  Hence the test statistic $T$ follows $T \sim t_{n-1}(\sqrt{n} \theta)$, where $\theta = \delta / \sigma$ and $\sigma^2$ is the variance of the contrast. We have $n_O = 153$ and $n_R = 49$.

  \paragraph{Study 27: \citet{Yap:2008fm}}
  The study has a $2 \times 2$ within-subject design. We are interested in the interaction. This is the same setup as Study 24 and thus we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have reanalyzed the replication data and confirmed that our test is equivalent. We have $n_O = 32$ and $n_R = 71$.

  \paragraph{Study 29: \citet{TurkBrowne:2008bg}}
  The test of interest is a one-sample $t$-test. We are testing if the observations has mean $0.5$. In other words, we want to test
  \[
  \delta = \mu - 0.5
  \]
  is zero. Hence the test statistic $T$ follows $T \sim t_{n-1}(\sqrt{n} \theta)$, where $\theta = (\mu / 0.5) / \sigma$ and $\sigma^2$ is the variance of individual observations. We have $n_O = 8$ and $n_R = 15$.

  \paragraph{Study 32: \citet{White:2008fb}}
  The study has a $2 \times 3$ within-subject design. We are interested in the main effect of the first factor. In other words, we want to test if
  \[
  \delta = \mu_{1*} - \mu_{2*}
  \]
  is zero. A natural estimate for $\delta$ is
  \[
  \hdelta = \frac{1}{n} \sum \lambda' X^{(i)},
  \]
  where $\lambda' = (\frac{1}{3}, \frac{1}{3}, \frac{1}{3}, -\frac{1}{3}, -\frac{1}{3}, -\frac{1}{3})$ and $X^{(i)}$ is the observation $(X_{11}, X_{12}, X_{13}, X_{21}, X_{22}, X_{23})'$. We can view $\lambda' X^{(i)}$ as the observations and perform a one-sample $t$-test. We have reanalyzed the replication data and confirmed that our test is equivalent.

  Hence the test statistic $T$ follows $T \sim t_{n-1}(\sqrt{n} \theta)$, where $\theta = \delta / \sigma$ and $\sigma^2$ is the variance of $\lambda' X^{(i)}$. We have $n_O = 37$ and $n_R = 38$.

  \paragraph{Study 33: \citet{Farrell:2008hr}}
  The test of interest is a paired $t$-test, same as Study 3. We define $\theta$ similarly, and have $n_O = 40$ and $n_R = 40$.

  \paragraph{Study 36: \citet{Pacton:2008dj}}
  The study has a $2 \times 2 \times 2$ mixed design with the first two factors being between-subject and the third factor being within-subject. We are interested in the main effect of the third factor. In other words, we want to test if
  \[
  \delta = \mu_{**1} - \mu_{**2}
  \]
  is zero. A natural estimate for $\delta$ is
  \[
  \hdelta = \frac{1}{n_{11}} \sum_{i \in I_{11}} \lambda' X^{(i)} + \frac{1}{n_{12}} \sum_{i \in I_{12}} \lambda' X^{(i)} + \frac{1}{n_{21}} \sum_{i \in I_{21}} \lambda' X^{(i)} + \frac{1}{n_{22}} \sum_{i \in I_{22}} \lambda' X^{(i)}
  \]
  where $\lambda' = (\frac{1}{4}, -\frac{1}{4})$ and $X^{(i)} = (X_{\cdot \cdot 1}, X_{\cdot \cdot 2})'$ for subject $i$. We can view $\lambda' X_{(i)}$ as the observations and assume that it has the same variance $\sigma^2$ across the groups. The variance of $\hdelta$ is thus $(\frac{1}{n_{11}} + \frac{1}{n_{12}} + \frac{1}{n_{21}} + \frac{1}{n_{22}}) \sigma^2$, and $\sigma^2$ can be estimated with the pooled variance. Hence we can test if $\delta = 0$ with a $t$-test with the distribution
  \[
  T = \frac{\hdelta}{\sqrt{\frac{1}{n_{11}} + \frac{1}{n_{12}} + \frac{1}{n_{21}} + \frac{1}{n_{22}}} \hsigma} \sim t_{n_{11} + n_{12} + n_{21} + n_{22} - 4}\left(\left(\frac{1}{n_{11}} + \frac{1}{n_{12}} + \frac{1}{n_{21}} + \frac{1}{n_{22}}\right)^{-1/2} \theta\right),
  \]
  where $\theta = \delta / \sigma$. We have reanalyzed the replication data and confirmed that our test is equivalent. We have
  \[
  \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_O = \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_R = \begin{bmatrix}
  6 & 6 \\
  6 & 6
  \end{bmatrix}.
  \]

  \paragraph{Study 49: \citet{Albarracin:2008em}}
  The study has a one-way (two-cell) between-subject design. In other words, we can use a two-sample $t$-test on the observations. We have reanalyzed the replication data and confirmed that our test is equivalent. Hence the test statistic $T$ follows $T \sim t_{n_1 + n_2 - 2} \left(\left(\frac{1}{n_1} + \frac{1}{n_2}\right)^{-1/2} \theta\right)$, where $\theta = (\mu_1 - \mu_2) / \sigma$. We have $n_{1O} + n_{2O} = 36$, $n_{1R} = 39$ and $n_{2R} = 49$, but $n_{1O}$ and $n_{2O}$ are unavailable.

  \paragraph{Study 52: \citet{Centerbar:2008vx}}
  The original study has a $2 \times 3$ mixed design with the first factor being between-subject and the second factor being within-subject. We are interested in the interaction. The original study compared a linear trend which amounts to applying a linear contrast for the second factor, and reported a $F(1, \cdot)$-statistic. The replication code (\url{https://osf.io/g29pw/}) does not use a linear contrast and produces a $F(2, \cdot)$-statistic instead. However the $F(1, \cdot)$-statistic for the replication, as recorded on the RP:P dataset can be produced if we apply the contrast, which amounts to omitting the second level of the second factor. We will thus consider this, a $2 \times 2$ mixed design, as the setup. This is the same setup as Study 4 and thus we define $\delta$, $\theta$, $\sigma^2$ similarly. We have $n_{1O} + n_{2O} = 133$, $n_{1R} = 59$ and $n_{2R} = 54$.

  \paragraph{Study 53: \citet{Amodio:2008fx}}
  The study has a $2 \times 2$ mixed design with the first factor being between-subject and the second factor being within-subject. We are interested in the interaction. This is the same setup as Study 4, and hence we defined $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_{1O} = 16$, $n_{2O} = 15$, $n_{1R} = 29$ and $n_{2R} = 46$.

  \paragraph{Study 56: \citet{vanDijk:2008br}}
  The original study has a $2 \times 2$ between-subject design and we are interested in the main effect of the first factor on one of the second factor's level. This can be still be thought of as a two-sample $t$-test, except variance is estimated by pooling all four groups. The replication used a two-sample $t$-test that directly compare those two cells. We have $n_{11O} + n_{12O} + n_{21O} + n_{22O} = 103$ and $n_{11R} = n_{21R} = 20$, but $n_{11O}$ and $n_{21O}$ are not available.

  \paragraph{Study 58: \citet{Lemay:2008jb}}
  The study has a $2 \times 2$ mixed design with the first factor being within-subject and the second factor being between-subject. We are interested in the interaction. This is the same setup as Study 4, and hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_{1O} = 123$, $n_{2O} = 63$, $n_{1R} = 192$ and $n_{2R} = 88$.

  \paragraph{Study 61: \citet{ErsnerHershfield:2008dt}}
  The test of interest is a two-sample $t$-test, same as Study 49. Hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_{1O} = 59$, $n_{2O} = 51$, $n_{1R} = 113$ and $n_{2R} = 110$.

  \paragraph{Study 63: \citet{Correll:2008cj}}
  The study has a one-way (two-cell) between-subject design, same as Study 49. Hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_{1O} \approx \frac{71}{3}$, $n_{2O} \approx \frac{71 \times 2}{3}$, $n_{1R} = 48$ and $n_{2R} = 100$.

  \paragraph{Study 65: \citet{Exline:2008dj}}
  The study has a $2 \times 2$ between-subject design and we are interested in the interaction. In other words, we want to test if
  \[
  \delta = \mu_{11} - \mu_{12} - \mu_{21} + \mu_{22}
  \]
  is zero. A natural estimate for $\delta$ is
  \[
  \hdelta = \frac{1}{n_{11}} \sum_{i \in I_{11}} X_i - \frac{1}{n_{12}} \sum_{i \in I_{12}} X_i - \frac{1}{n_{21}} \sum_{i \in I_{21}} X_i + \frac{1}{n_{22}} \sum_{i \in I_{22}} X_i.
  \]
  If we assume that the observations has the same variance $\sigma^2$ across the groups, then the variance of $\hdelta$ is thus $(\frac{1}{n_{11}} + \frac{1}{n_{12}} + \frac{1}{n_{21}} + \frac{1}{n_{22}}) \sigma^2$, and $\sigma^2$ can be estimated with the pooled variance. Hence we can test if $\delta = 0$ with a $t$-test using the distribution
  \[
  T = \frac{\hdelta}{\sqrt{\frac{1}{n_{11}} + \frac{1}{n_{12}} + \frac{1}{n_{21}} + \frac{1}{n_{22}}} \hsigma} \sim t_{n_{11} + n_{12} + n_{21} + n_{22} - 4}\left(\left(\frac{1}{n_{11}} + \frac{1}{n_{12}} + \frac{1}{n_{21}} + \frac{1}{n_{22}}\right)^{-1/2} \theta\right),
  \]
  where $\theta = \delta / \sigma$. We have reanalyzed the replication data and confirmed that our test is equivalent. We have
  \[
  \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_O = \begin{bmatrix}
  25 & 20 \\
  58 & 52
  \end{bmatrix}, \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_R = \begin{bmatrix}
  31 & 33 \\
  24 & 47
  \end{bmatrix}.
  \]

  \paragraph{Study 68: \citet{Risen:2008jo}}
  The study has a $2 \times 2$ between-subject design and we are interested in the interaction. This is the same setup as in Study 65, hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have
  \[
  \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_O = \begin{bmatrix}
  40 & 40 \\
  40 & 40
  \end{bmatrix}, \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_R = \begin{bmatrix}
  68 & 59 \\
  46 & 53
  \end{bmatrix}.
  \]

  \paragraph{Study 71: \citet{Stanovich:2008cm}}
  The test of interest is a two-sample $t$-test, same as Study 49. Hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_{1O} = 116$, $n_{2O} = 259$, $n_{1R} = 77$ and $n_{2R} = 100$.

  \paragraph{Study 72: \citet{Blankenship:2008ko}}
  The study has a $2 \times 2$ between-subject design and we are interested in the interaction. This is the same setup as in Study 65, hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have
  \[
  \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_O \approx \begin{bmatrix}
  \frac{261}{4} & \frac{261}{4} \\
  \frac{261}{4} & \frac{261}{4}
  \end{bmatrix}, \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_R = \begin{bmatrix}
  64 & 61 \\
  62 & 64
  \end{bmatrix}.
  \]

  \paragraph{Study 81: \citet{Shnabel:2008ck}}
  The study has a $2 \times 2$ between-subject design and we are interested in the interaction. This is the same setup as in Study 65, hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have
  \[
  \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_O \approx \begin{bmatrix}
  \frac{94}{4} & \frac{94}{4} \\
  \frac{94}{4} & \frac{94}{4}
  \end{bmatrix}, \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_R = \begin{bmatrix}
  33 & 34 \\
  37 & 37
  \end{bmatrix}.
  \]

  \paragraph{Study 87: \citet{Goff:2008ho}}
  The study has a $2 \times 2$ between-subject design and we are interested in the interaction. This is the same setup as in Study 65, hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have
  \[
  n_{11O} + n_{12O} + n_{21O} + n_{22O} = 55, \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_R = \begin{bmatrix}
  12 & 14 \\
  13 & 12
  \end{bmatrix},
  \]
  but the original cell sizes are unavailable.

  \paragraph{Study 94: \citet{McCrea:2008wu}}
  The test of interest is a two-sample $t$-test, same as Study 49. Hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_{1O} = 13$, $n_{2O} = 15$, $n_{1R} = 29$ and $n_{2R} = 32$.

  \paragraph{Study 97: \citet{PurdieVaughns:2008en}}
  The study has a $2 \times 2$ between-subject design and we are interested in the interaction. This is the same setup as in Study 65, and hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have
  \[
  \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_O \approx \begin{bmatrix}
  \frac{37}{2} & \frac{37}{2} \\
  \frac{40}{2} & \frac{40}{2}
  \end{bmatrix}, \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_R = \begin{bmatrix}
  691 & 679 \\
  57 & 63
  \end{bmatrix},
  \]

  \paragraph{Study 106: \citet{Dessalegn:2008gh}}
  The original study has a $2 \times 3$ mixed design with the first factor being between-subject and the second factor being within-subject. We are interested in the main effect of the first factor. This is equivalent to a two-sample $t$-test with all samples in each group pooled together. The replication used a two-sample $t$-test directly, same as Study 49. Hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_{1O} = 24$, $n_{2O} = 12$, $n_{1R} = 31$ and $n_{2R} = 16$.

  \paragraph{Study 107: \citet{Eitam:2008cm}}
  The test of interest is a two-sample $t$-test, same as Study 49. Hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_{1O} = 41$, $n_{2O} = 45$, $n_{1R} = 79$ and $n_{2R} = 79$.

  \paragraph{Study 110: \citet{Farris:2008ev}}
  While the original study used general linear model, the replication supposedly used the same model and ended up using ANOVA. We assume this is the correct analysis for the original study as well.

  The replication study has a $2 \times 2$ mixed design with the first factor being within-subject and the second factor being between-subject. We are interested in the interaction. This is the same setup as Study 4, and hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_{1O} = 178$, $n_{2O} = 102$, $n_{1R} = 65$ and $n_{2R} = 79$.

  \paragraph{Study 111: \citet{Janiszewski:2008kg}}
  The study has a $2 \times 2$ between-subject design. However the RP:P dataset does not match the original article in that the effect being investigated is in fact the interaction. Fortunately, since the replication data is available, we can reanalyze to obtain an interaction effect of $F(1, 116) = 0.01318$, $p = 0.9088$.

  This is the same setup as in Study 65, hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have
  \[
  n_{11O} + n_{12O} + n_{21O} + n_{22O} = 59, \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_R = \begin{bmatrix}
  30 & 30 \\
  30 & 30
  \end{bmatrix},
  \]
  but the original cell sizes are unavailable.

  \paragraph{Study 113: \citet{Armor:2008jp}}
  The test of interest is a one-sample $t$-test. We are testing if the observations has mean $0$. Hence the test statistic $T$ follows $T \sim t_{n-1} (\sqrt{n} \theta)$, where $\theta = \mu / \sigma$ and $\sigma^2$ is the variance of individual observations. We have $n_O = 125$ and $n_R = 176$.

  \paragraph{Study 114: \citet{Addis:2008hf}}
  The study has a $2 \times 2 \times 2$ mixed design with the first two factors being within-subject and the third factor being between-subject. We are interested in the main effect of the third factor. In other words, we want to test if
  \[
  \delta = \mu_{**1} - \mu_{**2}
  \]
  is zero. A natural estimate is
  \[
  \hdelta = \frac{1}{n_1} \sum_{i \in I_1} \lambda' X^{(i)} - \frac{1}{n_2} \sum_{i \in I_2} \lambda' X^{(i)}
  \]
  where $\lambda' = (\frac{1}{4}, \frac{1}{4}, \frac{1}{4}, \frac{1}{4})$ and $X^{(i)}$ is the observation $(X_{11 \cdot}, X_{12 \cdot}, X_{21 \cdot}, X_{22 \cdot})'$ for subject $i$. We can view $\lambda' X^{(i)}$ as the observations and perform a two-sample $t$-test. We have reanalyzed the replication data and confirmed that our test is equivalent.

  Hence the test statistic $T$ follows $T \sim t_{n_1 + n_2 - 2}\left(\left(\frac{1}{n_1} + \frac{1}{n_2}\right)^{-1/2} \theta\right)$, where $\theta = \delta / \sigma$ and $\sigma^2$ is the variance of $\lambda' X^{(i)}$. We have $n_{1O} = n_{2O} = n_{1R} = n_{2R} = 16$.

  \paragraph{Study 115: \citet{Nurmsoo:2008jq}}
  The test of interest is a one-sample $t$-test, same as Study 113. We have $n_O = 32$ and $n_R = 8$.

  \paragraph{Study 116: \citet{Vul:2008cz}}
  The test of interest is a paired $t$-test, same as Study 3. We define $\theta$ similarly, and have $n_O = 173$ and $n_R = 140$ \citep{Steegen:2014ii}.

  \paragraph{Study 118: \citet{Masicampo:2008jl}}
  The study has a $2 \times 2 \times 2$ between-subject design and we are interested in a particular contrast. We want to test if
  \[
  \delta = - (\mu_{111} - \mu_{112}) - (\mu_{121} - \mu_{122}) - (\mu_{221} - \mu_{222}) + 3 (\mu_{211} - \mu_{212}).
  \]
  is zero. A natural estimate $\hdelta$ is obtained by estimating each population cell mean with its sample cell mean. If we assume that the observations has the same variance $\sigma^2$ across the groups, then the variance of $\hdelta$ is thus $(\frac{1}{n_{111}} + \frac{1}{n_{112}} + \frac{1}{n_{121}} + \frac{1}{n_{122}} + \frac{9}{n_{211}} + \frac{9}{n_{212}} + \frac{1}{n_{221}} + \frac{1}{n_{222}}) \sigma^2$, and $\sigma^2$ can be estimated with the pooled variance. Hence we can test if $\delta = 0$ with a $t$-test using the distribution
  \begin{align*}
  T & = \frac{\hdelta}{\sqrt{\frac{1}{n_{111}} + \frac{1}{n_{112}} + \frac{1}{n_{121}} + \frac{1}{n_{122}} + \frac{9}{n_{211}} + \frac{9}{n_{212}} + \frac{1}{n_{221}} + \frac{1}{n_{222}}} \hsigma} \\
  & \sim t_{n-8}\left(\left(\frac{1}{n_{111}} + \frac{1}{n_{112}} + \frac{1}{n_{121}} + \frac{1}{n_{122}} + \frac{9}{n_{211}} + \frac{9}{n_{212}} + \frac{1}{n_{221}} + \frac{1}{n_{222}}\right)^{-1/2} \theta\right)
  \end{align*}
  where $\theta = \delta / \sigma$. We have reanalyzed the replication data and confirmed that our test is equivalent. We have
  \begin{align*}
  \begin{bmatrix}
  n_{111} & n_{112} & n_{121} & n_{122} \\
  n_{211} & n_{212} & n_{221} & n_{222}
  \end{bmatrix}_O & = \begin{bmatrix}
  14 & 20 & 13 & 14 \\
  20 & 13 & 13 & 13
  \end{bmatrix} \\
  \begin{bmatrix}
  n_{111} & n_{112} & n_{121} & n_{122} \\
  n_{211} & n_{212} & n_{221} & n_{222}
  \end{bmatrix}_R & = \begin{bmatrix}
  23 & 21 & 23 & 18 \\
  13 & 22 & 21 & 25
  \end{bmatrix}
  \end{align*}

  \paragraph{Study 121: \citet{Tabibnia:2008kq}}
  The original test of interest is a one-sample $t$-test while the replication test of interest is a $z$-test. We will the latter is the same test, except that the variance of the observation is known instead of estimated. This is the same setup as Study 29, and thus we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_O = 12$ and $n_R = 24$.

  \paragraph{Study 122: \citet{Alvarez:2008br}}
  The test of interest is a paired $t$-test, same as Study 3. We define $\theta$ similarly, and have $n_O = 8$ and $n_R = 17$.

  \paragraph{Study 124: \citet{Lau:2008td}}
  The study has a $2 \times 2$ mixed design with the first factor being between-subject and the second factor being within-subject. We are interested in the interaction. This is the same setup as Study 4, and hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_{1O} + n_{2O} = 36$, $n_{1R} = 34$ and $n_{2R} = 36$, but $n_{1O}$ and $n_{2O}$ are unavailable.

  \paragraph{Study 127: \citet{Winawer:2008jq}}
  The test of interest is a paired $t$-test, same as Study 3. We define $\theta$ similarly, and have $n_O = 29$ and $n_R = 26$.

  \paragraph{Study 133: \citet{Nairne:2008eb}}
  The study has a one-way (two-cell) within-subject design. Equivalently, we can use a paired $t$-test, same as Study 3. We define $\theta$ similarly, and have $n_O = 24$ and $n_R = 38$.

  \paragraph{Study 136: \citet{Vohs:2008kj}}
  The test of interest is a two-sample $t$-test, same as Study 49. Hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_{1O} \approx n_{2O} \approx 15$ and $n_{1R} = n_{2R} = 29$.

  \paragraph{Study 145: \citet{Halevy:2008gb}}
  The study has a $2 \times 2$ between-subject design and we are interested in the main effect of the first factor. In other words, we want to test if
  \[
  \delta = \mu_{1*} - \mu_{2*}
  \]
  is zero. A natural estimate of $\delta$ is
  \[
  \hdelta = \frac{1}{n_{11}} \sum_{i \in I_{11}} \frac{1}{2} X_i + \frac{1}{n_{12}} \sum_{i \in I_{12}} \frac{1}{2} X_i - \frac{1}{n_{21}} \sum_{i \in I_{21}} \frac{1}{2} X_i - \frac{1}{n_{22}} \sum_{i \in I_{22}} \frac{1}{2} X_i
  \]
  where $X_i$ are the observations. We can view $\frac{1}{2} X_i$ as the observations and assume that it has the same variance $\sigma^2$ across the groups. The variance of $\hdelta$ is thus $(\frac{1}{n_{11}} + \frac{1}{n_{12}} + \frac{1}{n_{21}} + \frac{1}{n_{22}}) \sigma^2)$ and $\sigma^2$ can be estimated with the pooled variance. Hence we can test if $\delta = 0$ with a $t$-test with the distribution
  \[
  T = \frac{\hdelta}{\sqrt{\frac{1}{n_{11}} + \frac{1}{n_{12}} + \frac{1}{n_{21}} + \frac{1}{n_{22}})} \hsigma} \sim t_{n_{11} + n_{12} + n_{21} + n_{22} - 4} \left(\left(\frac{1}{n_{11}} + \frac{1}{n_{12}} + \frac{1}{n_{21}} + \frac{1}{n_{22}}\right)^{-1/2} \theta\right),
  \]
  where $\theta = \delta / \sigma$. We have reanalyzed the replication data and confirmed that our test is equivalent. We have
  \[
  \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_O \approx \begin{bmatrix}
  20 & 20 \\
  20 & 20
  \end{bmatrix}, \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_R = \begin{bmatrix}
  10 & 10 \\
  10 & 10
  \end{bmatrix}.
  \]

  \paragraph{Study 146: \citet{Janssen:2008ca}}
  The test of interest is a paired $t$-test, same as Study 3. We define $\theta$ similarly, and have $n_O = 15$, $n_R = 12$.

  \paragraph{Study 148 and 149: \citet{Bressan:2008cj}}
  The study has a $2 \times 2 \times 2$ mixed design with the first factor being within-subject and the second and third factors being between-subject. We are interested in the three-way interaction. In other words, we want to test if
  \[
  \delta = \mu_{111} - \mu_{112} - \mu_{121} - \mu_{211} + \mu_{122} + \mu_{212} + \mu_{221} - \mu_{222}
  \]
  is zero. A natural estimate of $\delta$ is
  \[
  \hdelta = \frac{1}{n_{11}} \sum_{i \in I_{11}} \lambda' X^{(i)} - \frac{1}{n_{12}} \sum_{i \in I_{12}} \lambda' X^{(i)} - \frac{1}{n_{21}} \sum_{i \in I_{21}} \lambda' X^{(i)} + \frac{1}{n_{22}} \sum_{i \in I_{22}} \lambda' X^{(i)},
  \]
  where $\lambda' = (1, -1)$ and $X^{(i)}$ is the observation $(X_{1 \cdot \cdot}, X_{2 \cdot \cdot})'$ for subject $i$. We can view $\lambda' X^{(i)}$ as the observations and assume that it has the same variance $\sigma^2$ across the groups. The variance of $\hdelta$ is thus $(\frac{1}{n_{11}} + \frac{1}{n_{12}} + \frac{1}{n_{21}} + \frac{1}{n_{22}}) \sigma$ and $\sigma^2$ can be estimated with the pooled variance. Hence we can test if $\delta = 0$ with a $t$-test with the distribution
  \[
  T = \frac{\hdelta}{\sqrt{\frac{1}{n_{11}} + \frac{1}{n_{12}} + \frac{1}{n_{21}} + \frac{1}{n_{22}}} \hsigma} \sim t_{n_{11} + n_{12} + n_{21} + n_{22} - 4}\left(\left(\frac{1}{n_{11}} + \frac{1}{n_{12}} + \frac{1}{n_{21}} + \frac{1}{n_{22}}\right)^{-1/2} \theta\right),
  \]
  where $\theta = \delta / \sigma$. We have reanalyzed the replication data and confirmed that our test is equivalent. For the original study, we have $n_{11O} + n_{12O} = 101$, $n_{21O} + n_{22O} = 97$ but the individual cell sizes are not known. For the two replications, we have
  \[
  \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_{\text{Study 148}} = \begin{bmatrix}
  93 & 50 \\
  75 & 45
  \end{bmatrix}, \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_{\text{Study 149}} = \begin{bmatrix}
  107 & 70 \\
  83 & 58
  \end{bmatrix}.
  \]

  \paragraph{Study 150: \citet{Forti:2008bq}}
  The study has a $2 \times 2 \times 2$ within-subject design and we are interested in the two-way interaction between the second and third factors. This is the same setup as Study 1 and hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_O = 14$ and $n_R = 19$.

  \paragraph{Study 151: \citet{Schnall:2008jz}}
  The study has a one-way (two-cell) between-subject design, same as Study 49. Hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have $n_{1O} = 21$, $n_{2O} = 22$, $n_{1R} = 68$ and $n_{2R} = 58$.

  \paragraph{Study 153: \citet{Palmer:2008gb}}
  The test of interest is a one-sample $t$-test, same as Study 113. We have $n_O = n_R = 8$.

  \paragraph{Study 158: \citet{Goschke:2008ey}}
  The study has a $2 \times 2 \times 2$ mixed design with the first two factors being within-subject and the third factor being between-subject. We are interested in the two-way interaction between the first two factors. In other words, we want to test if
  \[
  \delta = \mu_{11*} - \mu_{12*} - \mu_{21*} + \mu_{22*}
  \]
  is zero. A natural estimate of $\delta$ is
  \[
  \hdelta = \frac{1}{n_1} \sum_{i \in I_1} \lambda' X^{(i)} + \frac{1}{n_2} \sum_{i \in I_2} \lambda' X^{(i)}
  \]
  where $\lambda' = (\frac{1}{2}, -\frac{1}{2}, -\frac{1}{2}, \frac{1}{2})$ and $X^{(i)}$ is the observation $(X_{11\cdot}, X_{12\cdot}, X_{21\cdot}, X_{22\cdot})'$ for subject $i$. We can view $\lambda' X^{(i)}$ as the observations and assume that it has the same variance $\sigma^2$ across the groups. The variance of $\hdelta$ is thus $(\frac{1}{n_1} + \frac{1}{n_2}) \sigma^2$, and $\sigma^2$ can be estimated with the pooled variance. Hence we can test if $\delta = 0$ with a $t$-test with the distribution
  \[
  T = \frac{\hdelta}{\sqrt{\frac{1}{n_1} + \frac{1}{n_2}} \hsigma} \sim t_{n_1 + n_2 - 2} \left(\left(\frac{1}{n_1} + \frac{1}{n_2}\right)^{-1/2} \theta\right),
  \]
  where $\theta = \delta / \sigma$. We have reanalyzed the replication data and confirmed that our test is equivalent. We have $n_{1O} = n_{2O} = 20$, $n_{1R} = 46$ and $n_{2R} = 49$.

  \paragraph{Study 161: \citet{LoBue:2008cn}}

  The study has a $2 \times 2$ between-subject design and we are interested in the main effect of the second factor. This is the same setup as Study 145, and hence we define $\delta$, $\theta$ and $\sigma^2$ similarly. We have 
  \[
  \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_O \approx \begin{bmatrix}
  12 & 12 \\
  12 & 12
  \end{bmatrix}, \begin{bmatrix}
  n_{11} & n_{12} \\
  n_{21} & n_{22}
  \end{bmatrix}_R = \begin{bmatrix}
  12 & 13 \\
  11 & 12
  \end{bmatrix}.
  \]

  \paragraph{Study 167: \citet{Estes:2008ci}}
  The study has a one-way (two-cell) within-subject design. Equivalently, we can use a paired $t$-test, same as Study 3. We define $\theta$ similarly, and have $n_O = 18$ and $n_R = 22$.

\section{Correlations and regressions}

  For studies with one or more continuous independent variable, the strategy used in ANOVA above no longer applies. Suppose the true (partial) correlation coefficient is $r$, then we can take the effect size to be $\theta = \tanh^{-1}(r)$. By Fisher transformation, the sample (partial) correlation coefficient, $R$, approximately follows
  \[
    \sqrt{n-3-p} \tanh^{-1}(R) \sim N(\sqrt{n-3-p} \,\theta, 1),
    \]
  when $p$ independent variables are controlled for \citep{Fisher:1924ve}.

  \paragraph{Study 39: \citet{Pleskac:2008de}}
  The test contrasts correlated sample correlation coefficients as per \citet{Meng:1992vq}. The four sample correlation coefficients, $r_i$, and their Fisher transformed $z$-statistic, $Z_i$ are combined into a $z$-statistic by the formula
  \[
  Z = (Z_1 - Z_2 + Z_3 - Z_4) \sqrt{\frac{n - 3}{4 (1 - r_x) h}},
  \]
  where $r_x$ is taken to the median among correlations between the independent variables, $h$ is given by $(1 - f \overline{r^2}) / (1 - \overline{r^2})$, $f = (1 - r_x) / 2 (1 - \overline{r^2})$ and $\overline{r^2}$ is the average of $r_i^2$. $\theta = \EE[Z_1 - Z_2 + Z_3 - Z_4]$ is the parameter whose confidence interval is given in \citet{Meng:1992vq}, and will be the choice of effect size in our analysis. In other words, if we assume $r_x$ and $h$ is known, then the test statistic $Z$ approximately has distribution
  \[
  Z \sim N\left(\sqrt{\frac{n - 3}{4 (1 - r_x) h}} \,\theta, 1\right).
  \]
  We have $\left(\sqrt{\frac{n - 3}{4 (1 - r_x) h}}\right)_O = 6.926$ and $\left(\sqrt{\frac{n - 3}{4 (1 - r_x) h}}\right)_R = 7.824$.

  \paragraph{Study 44: \citet{Payne:2008bf}}
  The test statistic comes from comparing a linear model with two independent variables and the same linear model with the interaction term added. The effect is the partial correlation, between the dependent variable and the interaction, controlling for the two independent variables. We have reanalyzed the replication data and confirmed that this test is equivalent. From Fisher transformation for partial correlation \citep{Fisher:1924ve}, we have
  \[
  \sqrt{n - 5} \tanh^{-1}(R) \sim N(\sqrt{n - 5} \,\theta, 1),
  \]
  and $R_O = 0.3522$, $n_O = 71$, $R_R = -0.1502$ and $n_R = 180$.

  \paragraph{Study 48: \citet{Cox:2008gt}}
  The test statistic comes from determining the coefficient in a three independent variable model with full interaction. The $t$-statistic provided tests for the significance of the slope in the first variable when the second variable is one SD above its mean and the third variable is one SD below its mean. We can alternatively shift the second and third variables, making this desired point zero, and run the regression. The effect is thus the partial correlation of the first variable with the dependent variable, controlling for the other two variables, the three two-way interactions and the three-way interaction. We have
  \[
  \sqrt{n - 9} \tanh^{-1}(R) \sim N(\sqrt{n - 9} \,\theta, 1),
  \]
  and $R_O = -0.2255$, $n_O = 100$, $R_R = -0.05229$ and $n_R = 200$.

  \paragraph{Study 93: \citet{Murray:2008il}}
  The test statistic comes from testing the significance of the three-way interaction of two categorical and one continuous independent variables. The effect is thus the partial correlation of the three-way interaction with the dependent variable, controlling for the three independent variables and their pairwise two-way interactions. We have reanalyzed the replication data and confirmed that this test is equivalent. We have
  \[
  \sqrt{n - 9} \tanh^{-1}(R) \sim N(\sqrt{n - 9} \,\theta, 1),
  \]
  and $R_O = 0.3175$, $n_O = 91$, $R_R = -0.1351$ and $n_R = 76$.

  \paragraph{Study 112: \citet{McKinstry:2008ez}}
  The original test statistic is a $F(1, \cdot)$-statistic coming from a simple regression. The effect is the correlation of the independent variable with the dependent variable. The original study provided $R_O = -0.70$ with $n_O = 11$ points in the regression. The replication gives $R_R = -0.1707$ and $n_R = 11$.

  \paragraph{Study 120: \citet{Hajcak:2008kw}}
  Suppose the true correlation coefficient is $r$ and the joint distribution of the variables is bivariate Gaussian. We have
  \[
  \sqrt{n-3} \tanh^{-1}(R) \sim N(\sqrt{n-3} \,\theta, 1),
  \]
  and $n_O = 31$ and $n_R = 43$.

  \paragraph{Study 134: \citet{Larsen:2008tu}}
  The original test statistic is a $t$-statistic from a regression. The effect is the partial correlation of an independent variable with the dependent variable, controlling for another independent variable. We have
  \[
  \sqrt{n - 4} \tanh^{-1}(R) \sim N(\sqrt{n - 4} \,\theta, 1),
  \]
  and $n_O = 119$ and $n_R = 238$.

  \paragraph{Study 154: \citet{Heine:2008fx}}
  Since the independent variables are in fact the same sample for all eight sample correlation coefficients, we do not agree with the analysis method implemented in \url{https://osf.io/akv6y/} in that the resulting test statistic is not a $z$-score with unit variance. Nonetheless, if we assume the analysis is done correctly here, then by Fisher transformation the test statistic will follow
  \[
  Z \sim N(\sqrt{n - 3} \,\theta, 1)
  \]
  for some parameter $\theta$ that does not vary with sample size. We will consider this $\theta$ as the effect size. We have $n_O = 70$ and $n_R = 16$.

  \paragraph{Study 155: \citet{Moeller:2008by}}
  The test statistic is a sample correlation coefficient, same as Study 120. We have $n_O = 53$ and $n_R = 72$.

\section{Normal approximation to \texorpdfstring{$t$}{t}-distribution}

  To investigate how well the normal approximation works to $t$-distributions, we first consider the typical degrees of freedom for the $t$-distributions. \Cref{fig:df} shows the degrees of freedom in the original and replication experiments where both are at least $30$. All but one study pair falls in the blue region, and hence the grid points marked by ``+'' are generally representative.
  \begin{figure}[htbp]
    \centering
    \includegraphics[width=0.5\textwidth]{df}
    \caption{Degrees of freedom in the original and replication experiments where both are at least $30$, on log-scale. The blue region covers all but one study pair, and hence the grid points we choose, marked as ``+'', are generally representative.}
  \label{fig:df}
  \end{figure}

  For each grid point, we simulate a pair of one-sided $t$-tests with the same effect sizes. We generate
  \[
    T_O \sim t_{df_O}(\text{ncp}_O) 1_{\{|T_O| > t_{df_O, \alpha/2}\}} \qquad \text{ and } \qquad T_R \sim t_{df_R}(\text{ncp}_R).
  \]
  Since the original sample size is typically chosen to achieve a certain power, we assume $\text{ncp}_O$ stays small. The type I error rate of the selective $z$-test is given in red in \Cref{fig:t-approx}. The type I error rate can deviate from $0.05$ as the noncentrality parameter grows.
  \begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{t-approx}
    \caption{The type I error rate as a function of the noncentrality parameter, based on a simulation. The type I error rate of the simple selective $z$-test is in red, which can deviate from $0.05$ when the noncentrality parameter is large. The type I error rate of the selective $z$-test with our proposed finite sample correction is in blue, and stay mostly controlled. Extreme differences in degrees of freedom, as indicated by the gray background, is absent.}
  \label{fig:t-approx}
  \end{figure}

  This deviation is caused by inaccuracy of approximating a noncentral $t$-distribution with a location-shifted standard Gaussian. We propose a finite sample correction by approximating the distribution of $T_O$ with
  \[
    T_O \sim t_{df_O}(\text{ncp}_O) 1_{\{|T_O| > t_{df_O, \alpha/2}\}} \approx N\left(\text{ncp}_O, 1 + \frac{2\text{ncp}_O^2}{df_O}\right) 1_{\{|T_O| > t_{df_O, \alpha/2}\}}
  \]
  and approximating the distribution of $T_R$ similarly. Note that the distribution of the test statistic relies on the unknown noncentrality parameter, which we replace with a plug-in estimator based on $T_R$: $T_R$ can stand in for $\text{ncp}_R$, as well as $\text{ncp}_O$ through the common effect size. The resulting type I error rate behaves better and is given in blue in \Cref{fig:t-approx}.

  With the finite sample correction, five ($11\%$) studies are rejected. Controlling the false discovery rate at $0.10$, we apply Benjamini--Hochberg  procedure \citeyearpar{Benjamini:1995cd} and rule four ($9\%$) replication studies as inconsistent with the original studies, namely \citet{Dodson:2008ks,vanDijk:2008br,PurdieVaughns:2008en,Farris:2008ev}, generally in line with our results without the finite sample correction. \citet{Farris:2008ev} remains rejected at familywise error rate $0.05$. To check if our assumptions still hold reasonably well, we recreate \Cref{fig:t-approx} with the effective $p$-value threshold of $0.004$ ($=\frac{4}{46} \cdot 0.05$) used in Benjamini--Hochberg procedure and $0.001$ ($=\frac{1}{46} \cdot 0.05$), given in \Cref{fig:t-approx-bh} and \Cref{fig:t-approx-bonf} respectively.
  \begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{t-approx-bh}
    \caption{The type I error rate as a function of the noncentrality parameter, based on a simulation. The type I error rate of the simple selective $z$-test is in red, which can deviate from $0.004$ when the noncentrality parameter is large. The type I error rate of the selective $z$-test with our proposed finite sample correction is in blue. Extreme differences in degrees of freedom, as indicated by the gray background, is absent.}
  \label{fig:t-approx-bh}
  \end{figure}
  \begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{t-approx-bonf}
    \caption{The type I error rate as a function of the noncentrality parameter, based on a simulation. The type I error rate of the simple selective $z$-test is in red, which can deviate from $0.001$ when the noncentrality parameter is large. The type I error rate of the selective $z$-test with our proposed finite sample correction is in blue. Extreme differences in degrees of freedom, as indicated by the gray background, is absent.}
  \label{fig:t-approx-bonf}
  \end{figure}

  For sake of completeness, we repeat the above plots specifically for the outlier \citep[Study 97;][]{PurdieVaughns:2008en} with exceptionally large replication degree of freedom, in \Cref{fig:t-approx-pv}.
  \begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{t-approx-pv}
    \caption{The type I error rate as a function of the noncentrality parameter, based on a simulation. The type I error rate of the simple selective $z$-test is in red and the type I error rate of the selective $z$-test with our proposed finite sample correction is in blue. The error rate is evaluated for a test with the nominal level, the effective level from Benjamini--Hochberg procedure and from Bonferroni correction.}
  \label{fig:t-approx-pv}
  \end{figure}

  Our overestimate, underestimate and confidence interval for the proportion of effect sizes that declined remain the same, but we now estimate conservatively that $14$ ($30\%$) of the effect sizes declined by at least $20\%$ with a $95\%$ lower confidence bound of three ($7\%$).

\Urlmuskip=0mu plus 1mu\relax
\bibliographystyle{plainnat}
\bibliography{papers,additional}

\end{document}

### 2019-03-15 ecdf.R

@@ -1,0 +1,30 @@
+# load data and functions if df is not already there
+if (!exists("df.original") | !exists("df")) {
+  source("shared.R")
+}
+
+df.pval <- na.omit(df.original[, c("T_pval_USE..O.", "T_pval_USE..R.")])
+colnames(df.pval) <- c("Original", "Replication")
+df.pval <- df.pval %>% gather(key = "experiment", value = "value")
+
+pdf("fig/ecdf.pdf", width = 6, height = 4)
+ggplot(df.pval) +
+  geom_vline(xintercept = c(0, 1), col = "gray50", size = 0.2) +
+  geom_hline(yintercept = c(0, 1), col = "gray50", size = 0.2) +
+  stat_ecdf(
+    aes(x = value, group = experiment, color = experiment), na.rm = TRUE
+  ) +
+  labs(
+    x = expression(italic("p") * "-value"),
+    y = "Cumulative frequency",
+    color = "Experiment"
+  ) +
+  geom_vline(xintercept = alpha, col = c.red, lty = 2) +
+  annotate(
+    "text", x = 0.05, y = 0.15, parse = TRUE, col = c.red, hjust = -0.1,
+    label = expression(italic("p") * "=0.05")
+  ) +
+  scale_color_manual(values = c(c.red, c.blue)) +
+  coord_fixed() + 
+  theme_minimal()
+dev.off()

### 2019-03-15 effect-size-k.R

@@ -1,0 +1,85 @@
+cell2k <- function(...) {
+  n <- unlist(list(...))
+  1 / sqrt(sum(1 / n))
+}
+
+# Columns: study.num, k.O, k.R
+df.k <-
+  rbind(
+    # t-tests and ANOVAS ======================================================
+    c(1, sqrt(14), sqrt(29)),
+    c(2, sqrt(24), sqrt(24)),
+    c(3, sqrt(25), sqrt(32)),
+    c(4, cell2k(120, 120), cell2k(136, 134)),
+    c(5, sqrt(32), sqrt(48)),
+    c(6, sqrt(24), sqrt(32)),
+    c(7, sqrt(100), sqrt(15)),
+    c(8, cell2k(20, 19), cell2k(13, 20)),
+    c(10, cell2k(16, 16), cell2k(16, 15)),
+    c(11, sqrt(22), sqrt(30)),
+    c(15, sqrt(95), sqrt(242)),
+    c(19, cell2k(16, 16), cell2k(11, 10)),
+    c(20, cell2k(48, 48), cell2k(47, 61)),
+    c(24, sqrt(153), sqrt(49)),
+    c(27, sqrt(32), sqrt(71)),
+    c(29, sqrt(8), sqrt(15)),
+    c(32, sqrt(37), sqrt(38)),
+    c(33, sqrt(40), sqrt(40)),
+    c(36, cell2k(6, 6, 6, 6), cell2k(6, 6, 6, 6)),
+    c(49, cell2k(18, 18), cell2k(39, 49)),
+    c(52, cell2k(66.5, 66.5), cell2k(59, 54)),
+    c(53, cell2k(16, 15), cell2k(29, 46)),
+    c(56, cell2k(25.75, 25.75), cell2k(20, 20)),
+    c(58, cell2k(123, 63), cell2k(192, 88)),
+    c(61, cell2k(59, 51), cell2k(113, 110)),
+    c(63, cell2k(71 / 3, 142 / 3), cell2k(48, 100)),
+    c(65, cell2k(25, 20, 58, 52), cell2k(31, 33, 24, 47)),
+    c(68, cell2k(40, 40, 40, 40), cell2k(68, 59, 46, 53)),
+    c(71, cell2k(116, 259), cell2k(77, 100)),
+    c(72, cell2k(65.25, 65.25, 65.25, 65.25), cell2k(64, 61, 62, 64)),
[…]

### 2019-03-15 effect-size.R

@@ -1,0 +1,294 @@
+# load data and functions if df is not already there
+if (!exists("df.original") | !exists("df")) {
+  source("shared.R")
+}
+
+# Testing (naive, selective, BH) ==============================================
+df <- df %>%
+  dplyr::filter(
+    deg.O >= 30 | is.na(deg.O),
+    deg.R >= 30 | is.na(deg.R)
+  ) %>%
+  dplyr::mutate(
+    naive.p = naive.test(z.O, z.R, 1 / k.O, -1 / k.R),
+    naive.p = 2 * pmin(naive.p, 1 - naive.p),
+    # sel.1s.p is pval for H0: theta.O > theta.R
+    sel.p = sel.test(z.O, z.R, 1 / k.O, -1 / k.R, z.O.lo, z.O.hi),
+    # make it two sided
+    sel.p = 2 * pmin(sel.p, 1 - sel.p),
+    naive.rej = naive.p < alpha,
+    sel.rej = sel.p < alpha
+  )
+df$bh.p <- p.adjust(df$sel.p, method = "BH")
+df$bh.rej <- df$bh.p < fdp.cont
+df$holm.p <- p.adjust(df$sel.p, method = "holm")
+df$holm.rej <- df$holm.p < 0.05
+cat(
+  "======== Rejections ========",
+  "\nNaive test:", sum(df$naive.rej), "/", nrow(df), "=", mean(df$naive.rej),
+  "\nSelective test:", sum(df$sel.rej), "/", nrow(df), "=", mean(df$sel.rej),
+  "\nSelective test, adjusted with BH:",
+  sum(df$bh.rej), "/", nrow(df), "=", mean(df$bh.rej),
+  "\nSelective test, adjusted with Holm:",
+  sum(df$holm.rej), "/", nrow(df), "=", mean(df$holm.rej),
+  "\n"
+)
+
+# Predictive interval for theta.hat.R ==========================================
+df <- df %>%
+  dplyr::mutate(
+    z.R.lo = sel.pi(z.O, k.O, k.R, z.O.lo, z.O.hi, 1 - alpha / 2),
+    z.R.hi = sel.pi(z.O, k.O, k.R, z.O.lo, z.O.hi, alpha / 2),
+    z.R.lo.naive = naive.pi(z.O, k.O, k.R, 1 - alpha / 2),
+    z.R.hi.naive = naive.pi(z.O, k.O, k.R, alpha / 2),
[…]

### 2019-03-15 fdp.R

@@ -1,0 +1,103 @@
+# load data and functions if df is not already there
+if (!exists("df.original") | !exists("df")) {
+  source("shared.R")
+}
+
+# Storey"s method using [0.5, 1.0] to estimate ================================
+lambda <- 0.5
+alphas <- c(0.001, 0.005, 0.01, 0.05)
+
+# Estimates for V based on original, replication or combined p-values, also UCBs
+
+# When alpha < 0.05, refer to method in Appendix B
+B <- sum(df$adjp.O > lambda)
+# a is alpha / 0.05
+fdrs <- foreach(a = alphas[-length(alphas)] / alpha, .combine = "rbind") %do% {
+  beta <- (1 - lambda) / (1 - lambda + a)
+  R <- sum(df$adjp.O < a)
+  N <- R + B
+  # Estimate
+  gamma.hat <- (1 / beta - 1) * B / R
+  # UCB
+  Q <- sum(pbinom(B, 1:N, beta) >= level)
+  gamma.ucb <- (Q - B) / R
+  c(gamma.hat, gamma.ucb)
+}
+
+# When alpha = 0.05 refer to method in the methodology section
+R <- nrow(df)
+# for original
+# estimate for V
+V.O <- B / (1 - lambda)
+# ucb for V
+V.hi.O <- sum(pbinom(B, 1:R, 1 - lambda) >= level)
+# adding special row to fdrs
+fdrs <- rbind(fdrs, c(V.O / R, V.hi.O / R))
+
+# Computes the FDR based on replication and combined p-vals
+more.fdrs <- foreach(a = alphas / alpha, .combine = "rbind") %do% {
+  # shrink data set according to new alpha
+  df.tmp <-
+    df %>%
+    filter(adjp.O < a) %>%
+    mutate(adjp.O = adjp.O / a)
+  R <- nrow(df.tmp)
+  
+  # for replication
+  B.R <- sum(df.tmp$adjp.R > lambda)
+  # estimate for V
+  V.R <- B.R / (1 - lambda)
+  # ucb for V
+  V.hi.R <- sum(pbinom(B.R, 1:R, 1 - lambda) >= level)
+  
+  c(V.R / R, V.hi.R / R)
+}
+
+fdrs <- cbind(fdrs, more.fdrs)
+rownames(fdrs) <- alphas
+colnames(fdrs) <- c("Ori", "Ori UCB", "Rep", "Rep UCB")
+# Table 2, last row gives Table 1
+fdrs
+
[…]

### 2019-03-15 sel-bias-sim.R

@@ -1,0 +1,333 @@
+library(dplyr)
+library(foreach)
+library(ggplot2)
+library(tidyr)
+
+# colors
+c.red <- "#d7191c"
+c.blue <- "#2c7bb6"
+
+n <- 1000000
+thetas <- seq(0, 2, 0.05)
+alpha <- 0.05
+z.alpha.2 <- qnorm(alpha / 2, lower.tail = FALSE)
+
+# Naive assessment of directional claims ======================================
+
+neg.prob <- pnorm(-z.alpha.2, thetas)
+pos.prob <- pnorm(z.alpha.2, thetas, lower.tail = FALSE)
+naive.no.rep <- 1 - (neg.prob^2 + pos.prob^2) / (neg.prob + pos.prob)
+fdp.sim <- neg.prob / (neg.prob + pos.prob)
+df <-
+  data.frame(theta = thetas, naive.no.rep = naive.no.rep, fdp = fdp.sim) %>%
+  gather(key = "key", value = "fraction", -theta)
+
+pdf("fig/naive-same-dir.pdf", width = 4.5, height = 3)
+ggplot(df) +
+  geom_hline(yintercept = 0, size = 0.2, color = "gray50") +
+  geom_vline(xintercept = 0, size = 0.2, color = "gray50") +
+  geom_line(aes(x = theta, y = fraction, group = key, color = key)) +
+  scale_color_manual(
+    values = c(c.blue, c.red),
+    labels = c("original claim is false", "original claim not confirmed")
+  ) +
+  geom_hline(yintercept = 0.64, lty = 2, color = c.red) +
+  annotate(
+    "text", color = c.red, x = 0, y = 0.64, hjust = -0.1, vjust = -0.5,
+    label = "RP:P rate = 64%"
+  ) +
+  labs(x = expression(theta), y = "Rate (lower is better)", parse = TRUE) +
+  theme_minimal() +
+  theme(legend.position = "bottom", legend.title = element_blank()) +
+  scale_y_continuous(labels = scales::percent) +
+  guides(color = guide_legend(nrow = 1, byrow = TRUE))
+dev.off()
+
+# Simulation for naive CI coverage ============================================
+
+set.seed(20180715)
+
+x.rand <- rnorm(n)
+
+coverage <- foreach(theta = thetas, .combine = "c") %do% {
+  x <- x.rand + theta
[…]

### 2019-03-15 shared.R

@@ -1,0 +1,296 @@
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(grid)
+library(gridExtra)
+library(foreach)
+library(doParallel)
+registerDoParallel()
+
+# constants ===================================================================
+# level used in journal
+alpha <- 0.05
+# level used in our analysis for ucb / test
+level <- 0.05
+# fdp controlled
+fdp.cont <- 0.1
+# colors
+c.red <- "#d7191c"
+c.blue <- "#2c7bb6"
+
+# functions ===================================================================
+# plotting with common legend
+grid.arrange.shared.legend <-
+  function(...,
+           ncol = length(list(...)),
+           nrow = 1,
+           position = c("bottom", "right")) {
+    
+    plots <- list(...)
+    position <- match.arg(position)
+    g <-
+      ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
+    legend <- g[[which(sapply(g, function(x)
+      x$name) == "guide-box")]]
+    lheight <- sum(legend$height)
+    lwidth <- sum(legend$width)
+    gl <- lapply(plots, function(x)
+      x + theme(legend.position = "none"))
+    gl <- c(gl, ncol = ncol, nrow = nrow)
+    
+    combined <- switch(
+      position,
+      "bottom" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 1,
+        heights = unit.c(unit(1, "npc") - lheight, lheight)
+      ),
+      "right" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 2,
+        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
+      )
+    )
+    
+    grid.newpage()
+    grid.draw(combined)
+    
+    # return gtable invisibly
+    invisible(combined)
+  }
+
+# computes the one tailed naive pval
+one.tail.pval <- function(type, stat, deg, n) {
+  pval <- NA
[…]

### 2019-03-15 t-approx.R

@@ -1,0 +1,264 @@
+# load data and functions if df is not already there
+if (!exists("df.original") | !exists("df")) {
+  source("shared.R")
+}
+
+df <- df %>%
+  dplyr::filter(
+    deg.O >= 30 | is.na(deg.O),
+    deg.R >= 30 | is.na(deg.R)
+  )
+# Row 27 is an outlier for deg.R
+range.degs.O <- range(df$deg.O[-27], na.rm = TRUE)
+range.degs.R <- range(df$deg.R[-27], na.rm = TRUE)
+degs.O <-
+  round(exp(seq(log(range.degs.O[1]), log(range.degs.O[2]), length.out = 5)))
+degs.R <-
+  round(exp(seq(log(range.degs.R[1]), log(range.degs.R[2]), length.out = 5)))
+
+# Show distribution of dfs ====================================================
+pdf("fig/df.pdf", width = 4, height = 6)
+ggplot(df) +
+  geom_point(aes(x = deg.O, y = deg.R)) +
+  scale_x_continuous(trans = "log10") +
+  scale_y_continuous(trans = "log10") +
+  geom_point(
+    data = expand.grid(x = degs.O, y = degs.R), aes(x = x, y = y),
+    color = c.blue, shape = "+", size = 5
+  ) +
+  annotate(
+    "polygon", fill = c.blue, alpha = 0.25,
+    x =
+      c(
+        degs.O[1], degs.O[2], degs.O[3], degs.O[5], degs.O[5], degs.O[4],
+        degs.O[3], degs.O[1], degs.O[1]
+      ),
+    y =
+      c(
+        degs.R[3], degs.R[4], degs.R[5], degs.R[5], degs.R[3], degs.R[2],
+        degs.R[1], degs.R[1], degs.R[3]
+      )
+  ) +
+  labs(x = expression(df[O]), y = expression(df[R])) +
+  theme_minimal()
+dev.off()
+
+# Simulation ==================================================================
+
+# one-sample t-test simulation parameters
+ncps.O <- seq(0, 5, 0.1)
+# size of simulation
+m <- 1e5
+
+nom.levels <- c(level, level / 46 * 4, level / 46)
+filenames <- c("t-approx", "t-approx-bh", "t-approx-bonf")
+
+for (i in 1:3) {
+  nom.level <- nom.levels[i]
[…]

### 2019-03-15 paper.tex
link to public repo

@@
 
-  A git repository containing with the code generating the images in this article is available at \url{https://kenhung@bitbucket.org/kenhung/reproducibility-in-psychology.git}.
+  A git repository containing with the code generating the images in this article is available at \url{https://github.com/kenhungkk/assessing-replicability.git}.
+
+\section*{Supplement}
+
+  The supplement is available in the git repository, or directly on \url{https://github.com/kenhungkk/assessing-replicability/raw/public/supplement.pdf}.
 

### 2020-03-06 response.tex
accepted version

\documentclass[]{article}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{courier}
\usepackage[round]{natbib}
\usepackage{subcaption}
\usepackage{xcolor}

\DeclareMathOperator{\var}{var}
\DeclareMathOperator*{\argmax}{arg\,max}

\setlength{\parindent}{15pt}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\newcommand{\EE}{\mathbb{E}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand*{\vertbar}{\rule[-1ex]{0.5pt}{2.5ex}}
\newcommand*{\horzbar}{\rule[.5ex]{2.5ex}{0.5pt}}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\diag}{diag}

\newcommand{\KHComment}[1]{{\color{green!50!gray} (KH: #1)}}
\newcommand{\WFComment}[1]{{\color{red!50!gray} (WF: #1)}}

\begin{document}

\begin{itemize}

\item Kenneth Hung
\item Response to reviews
\item Reference: Statistical Methods for Replicability Assessment

\end{itemize}

We thank both referees for their thoughtful questions and helpful suggestions. Please find a point-by-point response below.

\section{Response to Reviewer 1}

\begin{itemize}

\item {\em The current paper provides some previously lacking statistical rigor in the analysis of an impactful replication study, and establishes that publication bias due to selection of significant effects is consistent with the observed findings. This is important because it provides one possible explanation or mechanism for this widely discussed outcome. I believe this aspect of the paper is important enough that it would make sense to include it as a focal point in the abstract of the paper.}

We agree and have added this to the abstract.

\item {\em I found the statement of Assumption 1 a bit confusing to parse. It’s a run-on sentence. The word ``literally'' can be omitted in the preceding paragraph as well.}

Noted and rewritten.

\item {\em The plots on the right sides of Figures 2--4 are excellent for providing intuition. Is there a way to make this intuition clear as well for the estimators of FDP? I suspect it should be obvious that the estimates of FDP will be lower than $64\%$ when applied to the RP:P data, perhaps there is a figure that would show this.}

We believe that Figure 6 is the best at delivering the intuition for where this conclusion came from, and we have added more detailed descriptions there now.

\end{itemize}

\section{Response to Reviewer 2}

\begin{itemize}

\item {\em Should these both be $35\%$? Do you mean that all of the $35\%$ that declined did so by at least $20\%$, or that $35\%$ of the $35\%$ that declined did so by at least $20\%$?}

For this data set the estimates for how many declined, and how many declined by $20\%$, happen to coincide, but we understand why this created confusion.

We mean that all of the $35\%$ that declined did so by at least $20\%$ (or at least, that our estimates for how many effects declined, and how many effects declined by $20\%$, happen to coincide). We understand why this created confusion, however, and we have replaced $20\%$ with $25\%$.

\item {\em You mention ``in contrast to the earlier internal comparison method'' (pg 12) but it’s not very clear what it refers to and the phrase doesn’t appear again in the paper. I think you mean the the estimator at the top of the page?}

Yes, that is what we meant. We have rewritten to clarify what we are referring to.

\item {\em In general, I found it quite easy to get lost in the notation. You might find a notation table useful for clarity.}

Thank you for this suggestion, we have added a table.

\item {\em You comment on the sizing of replication studies to achieve fixed power under the original effect size, and how this negatively impacts replication chances due to inflated original effect sizes. It seems like there could be a role for post-selection inference here to more appropriately size those replication studies. If so, it might be an interesting point for the discussion.}

Yes, we agree this is interesting and we have added to ``Future work'' section.

\item {\em As an aside, I would actually question Assumption 1. I think strongly significant results are often significantly easier to publish than studies with $p$-values near $0.05$. This would be in the opposite direction of the pile-up phenomenon that you mention, though certainly both could happen together in different regions of $p$-value. I suppose that if recent suggestions for a much lower significance threshold were accepted, Assumption 1 would likely hold more strongly.}

We agree that it would be better to have more detailed information about this, especially for meta-analyses of studies in the recent past or future. With all the attention paid to replicability recently, it is likely that scientists' application of the $5\%$ significance threshold has become less automatic since 2008, when the RP:P studies were published. A more sophisticated assumption can replace Assumption 1 if we have a model for the propensity for publication, e.g.\ \citet{Andrews:2018vh}. We hope future work can refine this. With the additional data from preprints and registered reports, it might be possible to try assessing how behavior is changing.

\bibliographystyle{plainnat}
\bibliography{papers,additional}

\end{itemize}

\end{document}

### 2020-03-06 paper.tex
accepted version

@@
-\documentclass[11pt]{article}
+\documentclass[aoas, preprint]{imsart}
+
 \usepackage{amsmath}
@@
 \usepackage{subcaption}
+\usepackage{tabularx}
 \usepackage{tikz}
@@
 \usepackage{xcolor}
+
+% arXiv number
+\arxiv{arXiv:1903.08747}
+
+% custom definitions
+\startlocaldefs
 
@@
 
-\newcommand{\WFcomment}[1]{{\color{red!40!gray} (WF: #1)}}
-\newcommand{\KHcomment}[1]{{\color{green!40!gray} (KH: #1)}}
-
-% Uncomment this line to get rid of my comments
-% \renewcommand{\WFcomment}[1]{}
-% \renewcommand{\KHcomment}[1]{}
+\endlocaldefs
 
@@
 
+\begin{frontmatter}
+
 \title{Statistical Methods for Replicability Assessment}
-\date{\today}
-\author{
-  Kenneth Hung\thanks{Department of Mathematics, University of California, Berkeley} \and
-  William Fithian\thanks{Department of Statistics, University of California, Berkeley}
-}
-\maketitle
+\runtitle{Statistical Methods for Replicability Assessment}
+
+\begin{aug}
+  \author{\fnms{Kenneth} \snm{Hung}\corref{}\ead[label=e1]{kenhung@berkeley.edu}}
+  \and
+  \author{\fnms{William} \snm{Fithian}\ead[label=e2]{wfithian@berkeley.edu}}
+
+  \runauthor{K. Hung and W. Fithian}
+
+  \affiliation{University of California, Berkeley}
+
+  \address{Department of Mathematics\\ 951 Evans Hall, Suite 3840\\ Berkeley, CA 94720-3840\\
+  \printead{e1}}
+
+  \address{Department of Statistics\\ 301 Evans Hall\\ Berkeley, CA 94720\\
+          \printead{e2}}
+
+\end{aug}
 
@@
   We apply techniques from multiple testing and post-selection inference to develop new methods that answer these questions while explicitly accounting for selection bias.
-Re-analyzing the RP:P data, we estimate that $22$ out of $68$ ($32\%$) original directional claims were false (upper confidence bound $47\%$); by comparison, we estimate that among claims significant at the stricter significance threshold $0.005$, only $2.2$ out of $33$ ($7\%$) were directionally false (upper confidence bound $18\%$).
-In addition, we compute selection-adjusted confidence intervals for the difference in effect size between original and replication studies and, after adjusting for multiplicity, identify five ($11\%$) which exclude zero (exact replication).
-We estimate that the effect size declined by at least $20\%$ in the replication study relative to the original study in $16$ of the $46$ ($35\%$) study pairs (lower confidence bound $11\%$).
-Our methods make no distributional assumptions about the true effect sizes.
+Our analyses suggest that the RP:P dataset is largely consistent with publication bias due to selection of significant effects.
+The methods in this paper make no distributional assumptions about the true effect sizes.
 \end{abstract}
+
+\begin{keyword}[class=MSC]
+\kwd[Primary ]{62F03}
+\kwd[; secondary ]{62P25}
+\end{keyword}
+
+\begin{keyword}
+\kwd{replicability}
+\kwd{multiple testing}
+\kwd{post-selection inference}
+\kwd{publication bias}
+\kwd{meta-analysis}
+\end{keyword}
+
+\end{frontmatter}
 
@@
 All three summary statistics were widely reported as indicating a dire crisis for the credibility of experimental psychology research.
-For example, the {\em Washington Post} reported that RP:P ``affirms that the skepticism [of published results] was warranted'' \citep{Achenbach:2015vi}; the {\em Economist} noted that OSC ``managed to replicate satisfactorily the results of only $39\%$ of the studies investigated'' \citep{Anonymous:uoQKTVTm}; and the {\em New York Times} reported that ``more than half of the findings did not hold up when retested'' \citep{Carey:2015wp}.
+For example, the {\em Washington Post} reported that RP:P ``affirms that the skepticism [of published results] was warranted'' \citep{Achenbach:2015vi}; the {\em Economist} noted that OSC ``managed to replicate satisfactorily the results of only $39\%$ of the studies investigated'' \citeyearpar{Anonymous:uoQKTVTm}; and the {\em New York Times} reported that ``more than half of the findings did not hold up when retested'' \citep{Carey:2015wp}.
 
@@
 \citeauthor{Gilbert:2016he}\ concluded that ``OSC seriously underestimated the reproducibility of psychological science,'' sparking further debate between defenders of OSC's conclusions \citep{Anderson:2016gs,Srivastava:2016,Nosek:2016} and the critics \citep{Gilbert:2016uv,Gilbert:2016th}.\footnote{While much of the ensuing discussion focused on the question of whether the confidence interval metric $53\%$ is too pessimistic, analogous criticisms apply to the ``significant replications'' metric of $64\%$ as well: the replication studies could be underpowered even when a true effect is present.}
+
+\subsection{Three definitions of replicability}
 
@@
 We also compute confidence intervals for the effect shift in each individual study pair and find that, after adjusting for multiplicity, about $11\%$ of the intervals exclude zero, an idealized null hypothesis of perfect replication.
-For effect decline, we find in aggregate that $35\%$ of the true effects declined, and $35\%$ declined by at least $20\%$.
+For effect decline, we find in aggregate that $35\%$ of the true effects declined, and $22\%$ declined by at least $25\%$.
 
@@
   \]
-  If $S_i = +1$ and $\rho=0.2$, for example, rejecting $H_i^{D,\rho}$ amounts to an assertion that $\theta_{i,R} < 0.8 \,\theta_{i,O}$, i.e.
-the true effect declined by more than $20\%$, or is negative.
+  If $S_i = +1$ and $\rho=0.25$, for example, rejecting $H_i^{D,\rho}$ amounts to an assertion that $\theta_{i,R} < 0.75 \,\theta_{i,O}$, i.e.
+the true effect declined by more than $25\%$, or is negative.
 
@@
 We provide two estimators (one overestimate and one underestimate) and confidence interval for the proportion of false $H_i^{D,\rho}$.
+
+  To facilitate the rest of the paper, we recapitulate the notations above in \Cref{tbl:notation}.
+  \begin{table}[htbp]
+    \centering
+    \begin{tabularx}{\textwidth}{lX}
+      \toprule
+      Symbol & Meaning \\
+      \midrule
+      $\theta_{i,O}$, $\theta_{i,R}$ & True effect sizes in the original and replication $i$-th studies \\
+      $\htheta_{i,O}$, $\htheta_{i,R}$ & Effect size estimates in the original and replication $i$-th studies \\
+      $\sigma_{i,O}$, $\sigma_{i,R}$ & Standard errors in the original and replication $i$-th studies \\
+      $S_i$ & Sign of the original $i$-th study \\
+      $H_i^{S,O}$, $H_i^{S,R}$ & Hypothesis that a type S error has occurred in the original and replication $i$-th studies  \\
+      $H_i^E = H_i^{E,0}$, $H_i^{E,\delta}$ & Hypothesis that the true effect has shifted by $\delta$ from the original to the replication $i$-th study \\
+      $H_i^{D,\rho}$ & Hypothesis that the true effect size has declined by no more than the fraction $\rho$ \\
+      \bottomrule
+    \end{tabularx}
+    \caption{Summary of notations introduced.}
+  \label{tbl:notation}
+  \end{table}
 
@@
   Model~\eqref{eq:trunc-model} assumes that results are only published if they achieved statistical significance at some conventional threshold level $\ao$, which is $0.05$ in our data.
-While this assumption is not literally true in the case of RP:P since some original $p$-values are above $0.05$, we note that the model can be relaxed to the following milder assumption:
+While this assumption is not true in the case of RP:P since some original $p$-values are above $0.05$, we note that the model can be relaxed to the following milder assumption:
   \begin{assumption}
     \label{ass:sig-enough}
-    $p_O < \ao$ is ``significant enough'': that is, not all results with significant $p$-values are necessarily published, but a result with $p_O < \ao$ would have been equally likely to be published (or selected for replication), had the $p$-value taken on some other statistically significant value.
+    $p_O < \ao$ is ``significant enough'': a result with $p_O < \ao$ would be equally likely to be published (or selected for replication), if the $p$-value were some other statistically significant value.
   \end{assumption}
 
-  If \Cref{ass:sig-enough} holds, then we can model the original test statistics as following their theoretical distribution, truncated to the event where the corresponding $p$-values are below $\ao$, as in Model~\ref{eq:trunc-model}.
+  \Cref{ass:sig-enough} allows some significant $p$-values to go unpublished.
+If it holds, then we can model the original test statistics as following their theoretical distribution, truncated to the event where the corresponding $p$-values are below $\ao$, as in Model~\ref{eq:trunc-model}.
 
@@
 Because $p$-hacking is such a vaguely defined practice, it is unclear how we might incorporate it into our model, but in any case there is no evidence of a pileup just below $0.05$ in the original RP:P studies (see \Cref{fig:fdp-original}).
+We will reconsider the validity of \Cref{ass:sig-enough} in \Cref{sec:discussion}.
 
@@
 We now discuss methods for inference on the directional FDP for those studies with $p_O < \alpha < \ao$, based on comparing the number of adjusted $p$-values below $\alpha$ with the number above $\lambda\ao$, for some $\lambda > \alpha/\ao$.
-We call this method the {\em external comparison method} in contrast to the earlier {\em internal comparison method}.
+We call this method the {\em external comparison method} in contrast to the earlier {\em internal comparison method} that bases on \eqref{eq:Bgest}.
 This method will be less conservative as we are not constrained to only using the $p$-values in $[0, \alpha)$.
@@
       \begin{bmatrix} D \\ M \end{bmatrix} =
-      \begin{bmatrix} \eta' \mu \\ \eta_\perp' \mu \end{bmatrix}
+      \begin{bmatrix} \eta' Z \\ \eta_\perp' Z \end{bmatrix}
       \sim N\left(
@@
     \end{subfigure}
-    \caption{Histograms of $p$-values.
-We estimate the expected number of true nulls in each bin by the method from \citet{Storey:2002vj}, shown by the horizontal red line.
+    \caption{Method from \citet{Storey:2002vj} as demonstrated using histograms of $p$-values.
+We estimate the number of true nulls by conservatively assuming that every hypothesis right of the vertical red line to be true.
+Since the $p$-value under the null is superuniform, on average there are fewer null hypotheses left of the line than right of the line.
+Our overestimate of the number of true nulls in each bin is shown by the horizontal red line.
 A net excess of $p$-values above this line means false directional claims.}
@@
 The underestimate, overestimate and the $90\%$ confidence interval are given in \Cref{fig:effect-decline-range}.
-For example, we estimate that $16$ of the $46$ effect sizes ($35\%$ (with a $95\%$ lower confidence bound $11\%$) decreased by at least $20\%$, even after adjusting for selection on measurement noise.
+For example, we estimate that $10$ of the $46$ effect sizes ($22\%$) decreased by at least $25\%$, even after adjusting for selection on measurement noise.
 Note that this does not exclude explanations by other forms of selection, e.g.\ selecting a large effect when there is a random effect.
@@
   First, selection for significance is an inevitable consequence of the current scientific process.
-Our adjustments for selection is admittedly crude, but necessitated by the limitations in the given data.
+Our adjustments for selection allows not only better analysis, but also more informed design of future replication studies, e.g.\ better power calculations for and sizing of replications.
+While these adjustments are admittedly crude, they are necessitated by the limitations in the given data.
 With more available information, a better model for selection can be used.
 For example, with the advancement of preregistration, we can use the external comparison method to produce less conservative estimates of the directional FDP at level $\alpha = 0.05$ if we have more information about statistically nonsignificant studies.
-With more replications carried out, we can estimate the publication bias model in \citet{Andrews:2018vh} more precisely; together with higher powered design in replications \citep[e.g.][]{Camerer:2018de}, we can enhance the precision of our estimators and power of our tests.
+With more replications carried out, we can estimate the publication bias model in \citet{Andrews:2018vh} more precisely, which allows different propensity for publication for different statistical significant $p$-values as opposed to \Cref{ass:sig-enough}.
+Together with higher powered design in replications \citep[e.g.][]{Camerer:2018de}, we can enhance the precision of our estimators and power of our tests.
 
@@
 
-\section*{Supplement}
-
-  The supplement is available in the git repository, or directly on \url{https://github.com/kenhungkk/assessing-replicability/raw/public/supplement.pdf}.
-
 \section*{Acknowledgment}
@@
   We thank Marcel A L M van Assen, Yoav Benjamini, Dean Eckles, Philip B Stark, Jacob Steinhardt, Jonathan Taylor, Alexa Tulett, Stefan Wager, Daniel Yekutieli, and Bin Yu for helpful comments and discussions.
+In addition, we are grateful to our two anonymous reviewers for their helpful suggestions which have improved the paper.
+
+\begin{supplement}
+  \sname{Supplement A}\label{suppA}
+  \stitle{Supplement to ``Statistical Methods for Replicability Assessment''}
+  \slink[url]{https://github.com/kenhungkk/assessing-replicability/raw/public/supplement.pdf}
+  \sdescription{We evaluate our approximation of $t$-distributions by normal distributions, as well as detail considerations made for individual studies.}
+\end{supplement}
 
 \Urlmuskip=0mu plus 1mu\relax
-\bibliographystyle{plainnat}
+\bibliographystyle{imsart-nameyear}
 \bibliography{papers,additional}

### 2020-03-06 effect-size.R

@@ -239,7 +239,7 @@ cat(
 )
 
 # test the null H^D: theta.O * (1 - rho) <= theta.R
-rhos <- seq(-1, 1, 0.1)
+rhos <- seq(-1, 1, 0.01)
 df.decline <- foreach(rho = rhos, .combine = "rbind") %do% {
   if (rho == 1) {
     # same as testing theta.R >= 0, which gives p-value complement to testing
